\section{The common group-scheme construction}

The three cyclic theories used in Chapter~2 share the same formal
construction. Let $H$ be a commutative group scheme over a scheme $S$, and let
$\varphi:H\to H$ be a finite \'etale surjective homomorphism with constant
kernel $G$. If $X$ is an $S$-scheme and $a:X\to H$ is a section, then
\[
T_a:=X\times_{a,H,\varphi}H
\]
is a $G$-torsor over $X$. In coordinates it is the torsor
$\varphi(Y)=a$. If $a'=a+\varphi(b)$ for a section $b:X\to H$, translation
by $b$ identifies $T_a$ with $T_{a'}$.

For Kummer theory one takes $H=\bG_m$ and $\varphi(z)=z^e$; for
Artin--Schreier theory, $H=\bG_a$ and $\varphi(z)=z^p-z$; and for
Artin--Schreier--Witt theory, $H=\bW_r$ and
$\varphi=F-\mathrm{id}$. This is why the three equations in Chapter~2 behave
in parallel.

\section{Kummer and Artin--Schreier theory}
\label{appendix:kummer_and_as_proofs}

Let $K$ be a complete discretely valued field with residue characteristic
$p>0$. If $(e,p)=1$ and $K$ contains $\mu_e$, the Kummer sequence
\[
1\longrightarrow\mu_e\longrightarrow\bG_m
\xrightarrow{(-)^e}\bG_m\longrightarrow1
\]
and Hilbert~90 give
\[
H^1(K,\mu_e)\cong K^\times/(K^\times)^e.
\]
The class of $a\in K^\times$ is represented by $T^e=a$, with
$\zeta\in\mu_e$ acting by $T\mapsto\zeta T$.

\begin{proof}[Proof of \Cref{theorem:kummer_ramification}]
Write $a=\pi^m u$ with $u\in\Oo_K^\times$. Replacing $a$ by an element of
the same class in $K^\times/(K^\times)^n$ changes $m$ by a multiple of $n$.
If $n\mid m$, we may therefore assume that $a=u$ is a unit. Since $n$ is
invertible in the residue field, Hensel's lemma shows that $u$ is an $n$-th
power in $K$ precisely when its residue is an $n$-th power; this is the
trivial case. Otherwise the extension is obtained by lifting the corresponding
separable residue-field extension and is unramified.

In general, if $y^n=a$, then $v_L(y)=m/n$ with respect to the extension of
$v_K$. Hence the subgroup of the value group generated by $\Z$ and $m/n$ has
index $n/\gcd(n,m)$ over $\Z$, which is the ramification index. When
$\gcd(n,m)=1$ this index is $n$, so the extension is totally ramified; it is
tame because $(n,p)=1$. The converse is the Kummer classification supplied by
the displayed cohomological isomorphism. See
\cite[Proposition~1.83]{koch1997algebraic} for the general statement.
\end{proof}

In characteristic $p$, the Artin--Schreier sequence
\[
0\longrightarrow\F_p\longrightarrow\bG_a
\xrightarrow{\wp}\bG_a\longrightarrow0,
\qquad \wp(z)=z^p-z,
\]
and additive Hilbert~90 give
\[
H^1(K,\Z/p\Z)\cong K/\wp(K).
\]
The class of $a\in K$ is represented by $X^p-X=a$, with
$c\in\F_p$ acting by $X\mapsto X+c$.

\begin{proof}[Proof of \Cref{theorem:artin_schreier_ramification}]
If $v_K(a)>0$, the convergent series
$u=-\sum_{i\geq0}a^{p^i}$ satisfies $u^p-u=a$, so the class is trivial. If
$v_K(a)=0$, the same argument removes every term of positive valuation. The
extension is therefore determined by the Artin--Schreier class of the residue
of $a$: it is trivial when this residue class vanishes and otherwise is the
unramified cyclic extension of degree $p$.

Suppose now that $v_K(a)=-m<0$ and $p\nmid m$, and let $y^p-y=a$. Since the
residue class cannot be removed by an Artin--Schreier change of variable, the
extension has degree $p$. Normalize $v_L$ so that $v_L|_K=pv_K$. The equation
gives $v_L(y)=-m$, so the extension is totally ramified. Choose integers
$1\leq c\leq p-1$ and $b$ with $-cm+bp=1$. Then
$\varpi_L=y^c\pi^b$ is a uniformizer. For a nontrivial
$\sigma\in\Gal(L/K)$, after rescaling the generator we have
$\sigma(y)=y+1$, and
\[
v_L\bigl(\sigma(\varpi_L)-\varpi_L\bigr)
=v_L\bigl(\pi^b((y+1)^c-y^c)\bigr)
=bp-(c-1)m=m+1.
\]
Thus the unique lower ramification break is $m$; for a cyclic group of order
$p$ this is also the unique upper break. Finally, the Artin--Schreier
cohomological classification gives every cyclic extension of degree $p$.
The reduced polynomial representative used in the last assertion is
constructed in the proof of \Cref{lemma:realization_over_Gm}(2) below.
\end{proof}

\section{Artin--Schreier--Witt bookkeeping}
\label{appendix:asw_development}

We retain the notation for Witt vectors from the beginning of this appendix.
For an $\F_p$-algebra $A$, Frobenius acts componentwise on $W_r(A)$.

\begin{definition}\label{definition:asw_operator}
The \textbf{Artin--Schreier--Witt operator} is
\[
\wp:=F-\mathrm{id},\qquad
\wp\vec u=F\vec u\ominus\vec u.
\]
It is an endomorphism of the additive group of $W_r(A)$ and commutes with
truncation and Verschiebung.
\end{definition}

\begin{lemma}[Witt bookkeeping]\label{lemma:witt_bookkeeping}
Let $A$ be an $\F_p$-algebra.
\begin{enumerate}[label=(\roman*)]
    \item The truncation $t:W_r(A)\to W_{r-1}(A)$ is a ring homomorphism
    commuting with $F$, hence with $\wp$, and
    $\ker(t)=V^{r-1}A$.
    \item The map $V^{r-1}:A\to W_r(A)$ is additive and
    $\wp\circ V^{r-1}=V^{r-1}\circ\wp$.
    \item For every $\vec a\in W_r(A)$ and $c\in A$,
    \[
    \vec a\oplus V^{r-1}(c)
    =(a_0,\dots,a_{r-2},a_{r-1}+c).
    \]
\end{enumerate}
\end{lemma}

\begin{proof}
The first two assertions follow from
\Cref{prop:witt_multiplication_by_p}. For (iii), apply the ghost principle
over $\Z[a_0,\dots,a_{r-1},c]$. If
$\vec b=(0,\dots,0,c)$ and $\vec s=\vec a\oplus\vec b$, then
$w_n(\vec b)=0$ for $n<r-1$, so induction gives $s_n=a_n$ for
$n\leq r-2$. At level $r-1$, the identity
$w_{r-1}(\vec b)=p^{r-1}c$ gives
$p^{r-1}s_{r-1}=p^{r-1}(a_{r-1}+c)$, hence
$s_{r-1}=a_{r-1}+c$. The resulting identity of universal integral
polynomials holds over every $A$.
\end{proof}

The last assertion is special to the top Verschiebung slice. Witt addition is
not componentwise in lower positions, and the carry polynomials in
\Cref{eq:witt_addition_shape} cannot in general be discarded.

\section{The ASW group scheme and classification}

The Witt addition polynomials make $\A^r_{\F_p}$ into the additive Witt
vector group scheme $\bW_r$. The operator $\wp=F-\mathrm{id}$ is an
endomorphism of $\bW_r$ and fits into an exact sequence for the \'etale
topology
\begin{equation}\label{eq:asw_lang_sequence}
0\longrightarrow W_r(\F_p)\cong\Z/p^r\Z
\longrightarrow\bW_r\xrightarrow{\wp}\bW_r\longrightarrow0.
\end{equation}

\begin{lemma}[ASW covers are \'etale torsors]
\label{lemma:asw_etale_torsor}
Let $A$ be an $\F_p$-algebra and $\vec g\in W_r(A)$. Then
\[
B:=A[\vec X]\big/\bigl(\wp\vec X\ominus\vec g\bigr)
\]
is finite free over $A$, with basis
$\{\prod_nX_n^{a_n}:0\leq a_n\leq p-1\}$, and is \'etale over $A$.
Translation by $W_r(\F_p)\cong\Z/p^r\Z$ makes $\Spec B$ a
$\Z/p^r\Z$-torsor over $\Spec A$.
\end{lemma}

\begin{proof}
By the triangular shape of Witt addition
(\Cref{eq:witt_addition_shape}), the $n$-th equation in
$\wp\vec X\ominus\vec g=0$ has the form
\[
X_n^p-X_n-g_n+C_n'(X_0,\dots,X_{n-1};g_0,\dots,g_{n-1})=0.
\]
Successively adjoining $X_0,\dots,X_{r-1}$ therefore makes $B$ finite free
over $A$ with the stated basis. The Jacobian matrix is lower triangular with
diagonal entries $-1$, so $B/A$ is \'etale. Moreover, this cover is the
pullback of $\wp:\bW_r\to\bW_r$ along the section $\vec g$. Its kernel is
$\{\vec u:F\vec u=\vec u\}=W_r(\F_p)$, and translation by this kernel makes
the pullback a torsor.
\end{proof}

\begin{theorem}[Artin--Schreier--Witt theory;
{\cite[\S3--4]{Thomas2005}}]
\label{theorem:asw_theory}
Let $M\supseteq\F_p$ be a field. There is a canonical isomorphism
\[
W_r(M)/\wp W_r(M)\;\xrightarrow{\ \cong\ }
H^1(M,\Z/p^r\Z).
\]
The class of $\vec g$ corresponds to the torsor
\[
\Spec M[\vec X]\big/\bigl(\wp\vec X\ominus\vec g\bigr).
\]
If the class has order $p^s$, the corresponding cyclic extension has degree
$p^s$; in particular the torsor is connected precisely when its class has
order $p^r$. Every cyclic extension of degree dividing $p^r$ arises in this
way.
\end{theorem}

\begin{proof}
Let $M^s$ be a separable closure of $M$ and
$\Gamma=\Gal(M^s/M)$. The triangular equations in the preceding proof show
that $\wp$ is surjective on $W_r(M^s)$ and that its kernel is
$W_r(\F_p)$. The connecting map sends the class of $\vec g$ to
\[
\sigma\longmapsto\sigma(\vec u)\ominus\vec u,
\qquad \wp\vec u=\vec g.
\]
This is a continuous homomorphism $\Gamma\to W_r(\F_p)$, independent of
the choices. It is injective on classes because a $\Gamma$-invariant solution
lies in $W_r(M)$. It is surjective by additive Hilbert~90, applied inductively
to
\[
0\longrightarrow M^s\xrightarrow{V^{r-1}}W_r(M^s)
\xrightarrow{t}W_{r-1}(M^s)\longrightarrow0.
\]
Thus $W_r(M)/\wp W_r(M)\cong H^1(M,\Z/p^r\Z)$. The order and
connectedness assertions follow from the correspondence between finite
constant-group torsors and continuous characters: the degree of the connected
field extension is the order of the image of the associated character.
\end{proof}

\begin{cor}\label{cor:asw_class_order_and_first_component}
Let $M\supseteq\F_p$ and let $\vec g\in W_r(M)$ have $g_0=0$. Then
$p^{r-1}[\vec g]=0$ in $W_r(M)/\wp W_r(M)$. Consequently, a class of
order $p^r$ has nonzero zeroth component in every representative.
\end{cor}

\begin{proof}
By \Cref{eq:witt_p_to_r_minus_1},
$p^{r-1}\vec g=(0,\dots,0,g_0^{p^{r-1}})=0$ already in $W_r(M)$.
\end{proof}

\section{The Schmid--Witt ramification formula}
\label{appendix:schmid_witt_reference}

The break formula stated in
\Cref{theorem:schmid_witt_break_formula} is due, for finite residue fields,
to Kanesaka--Sekiguchi \cite{KanesakaSekiguchi1979} and Thomas
\cite{Thomas2005}, building on Schmid \cite{Schmid1937} for $r=1$, and for
arbitrary perfect residue fields to Elder--Keating
\cite{ElderKeating2025}. We use it in one direction only: evaluating the
formula on one reduced representative computes the largest upper break; no
minimization over representatives is needed.

Reducedness prevents cancellation between Witt levels. Indeed, if two
nonzero pole orders $m_j$ and $m_{j'}$, with $j<j'$, contributed the same
weighted value, then
$m_{j'}=p^{j'-j}m_j$ would be divisible by $p$, contradicting reducedness.
For $r=1$ the formula is exactly the Artin--Schreier break computation.

\section{Reduced polynomial representatives}

\begin{definition}\label{definition:reduced_polynomial_vector}
A vector $\vec g=(g_0,\dots,g_{r-1})\in W_r(k((x)))$ is a
\textbf{reduced polynomial vector} if it is reduced and every
$g_j\in x^{-1}k[x^{-1}]$.
\end{definition}

\begin{lemma}[Surjectivity on integral Witt vectors]
\label{lemma:wp_surjective_on_integral_witt}
If $k$ is algebraically closed, then
$\wp:W_r(k[[x]])\to W_r(k[[x]])$ is surjective.
\end{lemma}

\begin{proof}
Proceed by induction on $r$. For $r=1$, given
$h=\sum_{i\geq0}b_ix^i$, choose $u_0$ with
$u_0^p-u_0=b_0$ and define the remaining coefficients recursively by
$u_i=u_{i/p}^p-b_i$, with $u_{i/p}=0$ when $p\nmid i$. Then
$u^p-u=h$.

For $r>1$, choose by induction $\vec u'\in W_{r-1}(k[[x]])$ with
$\wp\vec u'=t(\vec h)$ and lift it to
$\widetilde u=(\vec u',0)$. By \Cref{lemma:witt_bookkeeping}(i),
$\wp\widetilde u\ominus\vec h=V^{r-1}(g)$ for some $g\in k[[x]]$.
Choose $w\in k[[x]]$ with $\wp w=-g$. Then
\Cref{lemma:witt_bookkeeping}(ii) gives
$\wp(\widetilde u\oplus V^{r-1}w)=\vec h$.
\end{proof}

\begin{prop}[Reduced polynomial representatives]
\label{prop:reduced_polynomial_representatives}
Every class in $W_r(k((x)))/\wp W_r(k((x)))$ has a reduced polynomial
representative.
\end{prop}

\begin{proof}
Proceed by induction on $r$. For $r=1$, write a Laurent series as the sum of
its principal part and an element of $k[[x]]$. The latter can be removed by
\Cref{lemma:wp_surjective_on_integral_witt}. If the remaining principal part
has leading term $cx^{-m}$ with $p\mid m$, subtract
\[
\wp(c^{1/p}x^{-m/p})=cx^{-m}-c^{1/p}x^{-m/p}.
\]
This strictly decreases the pole order; iteration produces zero or a pole
order prime to $p$.

For the inductive step, first reduce the truncation of the given vector and
lift the change of representative to length $r$. The first $r-1$ components
are then reduced polynomials. By
\Cref{lemma:witt_bookkeeping}(iii), subtracting an element of the form
$\wp(V^{r-1}z)=V^{r-1}(\wp z)$ changes only the last component. Apply the
length-one procedure to that component: remove its integral part and then
successively remove leading terms whose pole orders are divisible by $p$.
This leaves all earlier components unchanged and produces a reduced polynomial
vector representing the original class.
\end{proof}

\begin{rem*}\label{rem:realization_Wr_sanity}
The Witt pole bound forces $f_j=0$ whenever $p^{r-1-j}\geq d$. Thus the
restriction imposed by a break smaller than $d$ is visible in every Witt
component, not only in the last one.
\end{rem*}
