\chapter{Cyclic Torsor Theories and Witt Vectors}
\label{appendix:witt_vector_algebra}
\label{appendix:cyclic_torsor_theories}

This appendix contains the supporting theory and proofs for the three cyclic
torsor descriptions stated in Chapter~2. We begin with the common
group-scheme construction and the classical Kummer and Artin--Schreier cases.
We then develop the finite-length \(p\)-typical Witt-vector algebra needed for
Artin--Schreier--Witt theory, followed by its torsor classification and
normal-form arguments. The final section isolates the weighted-homogeneity
property used in the cyclic symmetric-power calculation. The Schmid--Witt
ramification-break formula is stated, referenced, and applied in Chapter~2;
we do not reproduce its proof.

\providecommand{\bW}{\mathbb{W}}

\section{The common group-scheme construction}

The three cyclic theories used in Chapter~2 share the same formal
construction. Let $H$ be a commutative group scheme over a scheme $S$, and let
$\varphi:H\to H$ be a finite \'etale surjective homomorphism with kernel
$G$. If $X$ is an $S$-scheme and $a:X\to H$ is a section, then
\[
T_a:=X\times_{a,H,\varphi}H
\]
is a $G$-torsor over $X$. In coordinates it is the torsor
$\varphi(Y)=a$. If $a'=a+\varphi(b)$ for a section $b:X\to H$, translation
by $b$ identifies $T_a$ with $T_{a'}$.

For Kummer theory one takes $H=\bG_m$ and $\varphi(z)=z^e$; for
Artin--Schreier theory, $H=\bG_a$ and $\varphi(z)=z^p-z$; and for
Artin--Schreier--Witt theory, $H=\bW_r$ and
$\varphi=F-\mathrm{id}$. This is why the three equations in Chapter~2 behave
in parallel.

\section{Kummer and Artin--Schreier theory}
\label{appendix:kummer_and_as_proofs}

Let $K$ be a complete discretely valued field with residue characteristic
$p>0$.

\subsection{Kummer theory}

If $(e,p)=1$ and $K$ contains $\mu_e$, the Kummer sequence
\[
1\longrightarrow\mu_e\longrightarrow\bG_m
\xrightarrow{(-)^e}\bG_m\longrightarrow1
\]
and Hilbert~90 give
\[
H^1(K,\mu_e)\cong K^\times/(K^\times)^e.
\]
The class of $a\in K^\times$ is represented by $T^e=a$, with
$\zeta\in\mu_e$ acting by $T\mapsto\zeta T$.

\begin{proof}[Proof of \Cref{theorem:kummer_ramification}]
Write $a=\pi^m u$ with $u\in\Oo_K^\times$. Replacing $a$ by an element of
the same class in $K^\times/(K^\times)^n$ changes $m$ by a multiple of $n$.
If $n\mid m$, we may therefore assume that $a=u$ is a unit. Since $n$ is
invertible in the residue field, Hensel's lemma shows that $u$ is an $n$-th
power in $K$ precisely when its residue is an $n$-th power; this is the
trivial case. Otherwise the extension is obtained by lifting the corresponding
separable residue-field extension and is unramified.

In general, if $y^n=a$, then $v_L(y)=m/n$ with respect to the extension of
$v_K$. Hence the subgroup of the value group generated by $\Z$ and $m/n$ has
index $n/\gcd(n,m)$ over $\Z$, which is the ramification index. When
$\gcd(n,m)=1$ this index is $n$, so the extension is totally ramified; it is
tame because $(n,p)=1$. The converse is the Kummer classification supplied by
the displayed cohomological isomorphism. See
\cite[Proposition~1.83]{koch1997algebraic} for the general statement.
\end{proof}

\subsection{Artin--Schreier theory}

In characteristic $p$, the Artin--Schreier sequence
\[
0\longrightarrow\F_p\longrightarrow\bG_a
\xrightarrow{\wp}\bG_a\longrightarrow0,
\qquad \wp(z)=z^p-z,
\]
and additive Hilbert~90 give
\[
H^1(K,\Z/p\Z)\cong K/\wp(K).
\]
The class of $a\in K$ is represented by $X^p-X=a$, with
$c\in\F_p$ acting by $X\mapsto X+c$.

\begin{proof}[Proof of \Cref{theorem:artin_schreier_ramification}]
If $v_K(a)>0$, the convergent series
$u=-\sum_{i\geq0}a^{p^i}$ satisfies $u^p-u=a$, so the class is trivial. If
$v_K(a)=0$, the same argument removes every term of positive valuation. The
extension is therefore determined by the Artin--Schreier class of the residue
of $a$: it is trivial when this residue class vanishes and otherwise is the
unramified cyclic extension of degree $p$.

Suppose now that $v_K(a)=-m<0$ and $p\nmid m$, and let $y^p-y=a$. Since the
residue class cannot be removed by an Artin--Schreier change of variable, the
extension has degree $p$. Normalize $v_L$ so that $v_L|_K=pv_K$. The equation
gives $v_L(y)=-m$, so the extension is totally ramified. Choose integers
$1\leq c\leq p-1$ and $b$ with $-cm+bp=1$. Then
$\varpi_L=y^c\pi^b$ is a uniformizer. For a nontrivial
$\sigma\in\Gal(L/K)$, after rescaling the generator we have
$\sigma(y)=y+1$, and
\[
v_L\bigl(\sigma(\varpi_L)-\varpi_L\bigr)
=v_L\bigl(\pi^b((y+1)^c-y^c)\bigr)
=bp-(c-1)m=m+1.
\]
Thus the unique lower ramification break is $m$; for a cyclic group of order
$p$ this is also the unique upper break. Finally, the Artin--Schreier
cohomological classification gives every cyclic extension of degree $p$.
The reduced polynomial representative used in the last assertion is
constructed in the proof of \Cref{lemma:realization_over_Gm}(2).
\end{proof}

\begin{lemma}[Classical cyclic equations are \'etale torsors]
\label{lemma:classical_cyclic_equations_etale_torsors}
Let $A$ be a ring.
\begin{enumerate}[label=(\roman*)]
    \item If $n$ is invertible in $A$ and $a\in A^\times$, then
    \[
    A[T]/(T^n-a)
    \]
    is finite free over $A$, with basis $1,T,\dots,T^{n-1}$, and is
    \'etale over $A$. Multiplication of $T$ makes its spectrum a
    $\mu_n$-torsor over $\Spec A$.
    \item If $A$ is an $\F_p$-algebra and $a\in A$, then
    \[
    A[X]/(X^p-X-a)
    \]
    is finite free over $A$, with basis $1,X,\dots,X^{p-1}$, and is
    \'etale over $A$. Translation of $X$ makes its spectrum a
    $\Z/p\Z$-torsor over $\Spec A$.
\end{enumerate}
\end{lemma}

\begin{proof}
Both defining polynomials are monic, giving the stated bases and finite
freeness. In the Kummer algebra, $T$ is a unit because $T^n=a\in A^\times$;
therefore the derivative $nT^{n-1}$ is a unit. The derivative of
$X^p-X-a$ is $-1$. Thus both algebras are \'etale over $A$. They are the
pullbacks from Appendix~A.1 of $(-)^n:\bG_m\to\bG_m$ and
$\wp:\bG_a\to\bG_a$, respectively, so translation by the corresponding
kernels $\mu_n$ and $\F_p\cong\Z/p\Z$ gives the asserted torsor structures.
\end{proof}

\section{Witt-vector algebra}

\subsection{Ring structure and ghost coordinates}

For $n \geq 0$, the $n$-th \textbf{Witt polynomial} in the variables $X_0, \dots, X_n$
is
\[
w_n(X_0, \dots, X_n) \;=\; \sum_{j=0}^{n} p^j X_j^{p^{n-j}}
\;=\; X_0^{p^n} + p X_1^{p^{n-1}} + \dots + p^n X_n .
\]

\begin{theorem}[Witt; {\cite[II, \S6, Theorem~6]{serreLF}}, {\cite[\S1]{Rabinoff2014Witt}}]
\label{theorem:witt_ring_structure}
There exists a unique family of polynomials
$S_n, P_n \in \Z[X_0, \dots, X_n; Y_0, \dots, Y_n]$, $n \geq 0$, such that
\[
\begin{aligned}
w_n(S_0, \dots, S_n)
    &= w_n(X_0,\dots,X_n) + w_n(Y_0,\dots,Y_n),\\
w_n(P_0, \dots, P_n)
    &= w_n(X_0,\dots,X_n) \cdot w_n(Y_0,\dots,Y_n).
\end{aligned}
\]
for all $n$. For any commutative ring $A$, the operations
\[
\vec a \oplus \vec b := \bigl(S_n(\vec a; \vec b)\bigr)_{0 \le n \le r-1},
\qquad
\vec a \odot \vec b := \bigl(P_n(\vec a; \vec b)\bigr)_{0 \le n \le r-1}
\]
make the set $A^r$ into a commutative ring $W_r(A)$, the ring of \textbf{$p$-typical
Witt vectors of length $r$ over $A$}, with zero $(0, \dots, 0)$ and unit
$(1, 0, \dots, 0)$. Additive inverses are likewise given by universal integral
polynomials; we write $\ominus$ for Witt subtraction. The \textbf{ghost map}
\[
w \colon W_r(A) \longrightarrow A^r,
\qquad
\vec a \longmapsto \bigl(w_0(\vec a), w_1(\vec a), \dots, w_{r-1}(\vec a)\bigr)
\]
is a ring homomorphism to the product ring $A^r$; it is injective when $p$ is a
non-zero-divisor in $A$, and bijective when $p \in A^\times$.
\end{theorem}

We index the components of a Witt vector $\vec a = (a_0, \dots, a_{r-1})$ by
$0, \dots, r-1$. For $r = 1$ the polynomials reduce to $S_0 = X_0 + Y_0$ and
$P_0 = X_0 Y_0$, so $W_1(A) = A$ as a ring.

Since the ring operations are given by universal polynomials with integer
coefficients, $W_r$ is a functor: a ring homomorphism $\sigma \colon A \to B$ induces
the ring homomorphism
\[
W_r(\sigma) \colon W_r(A) \to W_r(B),
\qquad
W_r(\sigma)(a_0, \dots, a_{r-1}) = (\sigma a_0, \dots, \sigma a_{r-1}),
\]
acting \emph{componentwise}. Two consequences of this trivial-looking observation are
used repeatedly and deserve emphasis: a ring automorphism $\sigma$ of $A$ commutes
with $\oplus$ and $\ominus$ on $W_r(A)$, and a Witt vector $\vec a \in W_r(A)$
satisfies $W_r(\sigma)(\vec a) = \vec a$ if and only if \emph{each component} $a_n$ is
$\sigma$-invariant. In particular, for a group $\Gamma$ acting on $A$ by ring
automorphisms,
\begin{equation}\label{eq:witt_invariants_componentwise}
W_r(A)^{\Gamma} \;=\; W_r\bigl(A^{\Gamma}\bigr)
\qquad \text{inside } W_r(A).
\end{equation}

The uniqueness statement in \Cref{theorem:witt_ring_structure} is an instance of a
general principle that we invoke several times, so we record it explicitly.

\begin{lemma}[ghost principle]\label{lemma:ghost_principle}
Let $\Phi$ and $\Psi$ be two operations on Witt vectors given by universal polynomials
with integer coefficients in the components of their arguments. If
$w \circ \Phi = w \circ \Psi$ holds over the polynomial ring
$\Z[X_0, X_1, \dots]$ on the components of the arguments, then $\Phi = \Psi$ over
every commutative ring.
\end{lemma}

\begin{proof}
Over $\Z[X_0, X_1, \dots]$ the prime $p$ is a non-zero-divisor, so the ghost map is
injective by \Cref{theorem:witt_ring_structure} and $\Phi = \Psi$ there; this is an
identity of integral polynomials, which persists under every base change
$\Z[X_0, X_1, \dots] \to A$.
\end{proof}

The only structural feature of the addition polynomials $S_n$ that we shall need is
their ``triangular'' shape:

\begin{prop}[shape of Witt addition]\label{prop:witt_addition_shape}
For every $n \geq 0$ there is a polynomial
\[
C_n \in \Z[X_0, \dots, X_{n-1}; Y_0, \dots, Y_{n-1}]
\]
involving only the variables of index \emph{strictly less} than $n$, such that
\begin{equation}\label{eq:witt_addition_shape}
(\vec a \oplus \vec b)_n \;=\; a_n + b_n + C_n(a_0, \dots, a_{n-1}; b_0, \dots, b_{n-1}).
\end{equation}
We refer to $C_n$ as the \textbf{carry polynomial}. The analogous statement holds for
$\ominus$.
\end{prop}

\begin{proof}
By induction on $n$, using the recursion defining $S_n$:
\[
p^n S_n \;=\; \sum_{j \leq n} p^j \bigl(X_j^{p^{n-j}} + Y_j^{p^{n-j}}\bigr)
\;-\; \sum_{j < n} p^j S_j^{p^{n-j}} .
\]
The terms with $j = n$ contribute $p^n (X_n + Y_n)$, and all remaining terms involve
only variables and polynomials $S_j$ of index $j < n$, which by induction lie in
$\Z[X_{<n}; Y_{<n}]$. Since $S_n$ has integer coefficients
(\Cref{theorem:witt_ring_structure}), $C_n := S_n - X_n - Y_n$ is an integral
polynomial in the variables of index $< n$. The statement for $\ominus$ follows by the
same argument applied to the inversion polynomials.
\end{proof}

\subsection{Frobenius, Verschiebung, and truncation}

From now on, $A$ denotes an $\F_p$-algebra; this is the only case we use. Three
operators act on the rings $W_r(A)$:

\begin{definition}\label{definition:witt_operators}
Let $A$ be an $\F_p$-algebra.
\begin{enumerate}
    \item The \textbf{Frobenius} $F \colon W_r(A) \to W_r(A)$ is
    $F := W_r(\varphi_A)$, where $\varphi_A \colon a \mapsto a^p$ is the absolute
    Frobenius of $A$. Explicitly, $F$ acts componentwise:
    $F(a_0, \dots, a_{r-1}) = (a_0^p, \dots, a_{r-1}^p)$. By functoriality, $F$ is a
    ring endomorphism of $W_r(A)$.
    \item The \textbf{Verschiebung} is the shift
    \[
    V \colon W_{r-1}(A) \to W_r(A),
    \qquad
    V(a_0, \dots, a_{r-2}) = (0, a_0, \dots, a_{r-2}).
    \]
    Iterating, $V^j \colon W_{r-j}(A) \to W_r(A)$; in particular
    $V^{r-1} \colon A = W_1(A) \to W_r(A)$ sends $c \mapsto (0, \dots, 0, c)$.
    \item The \textbf{truncation} is
    \[
    t \colon W_r(A) \to W_{r-1}(A),
    \qquad
    t(a_0, \dots, a_{r-1}) = (a_0, \dots, a_{r-2}).
    \]
\end{enumerate}
\end{definition}

\begin{rem*}
For a general (not necessarily $\F_p$-) algebra $A$, the Frobenius is defined by
universal polynomials characterized by $w_n \circ F = w_{n+1}$, and the componentwise
formula above holds precisely in characteristic $p$; see
\cite[II, \S6]{serreLF} or \cite[\S2]{Rabinoff2014Witt}. We will not need the general
case.
\end{rem*}

We record from the general theory (\cite[II, \S6]{serreLF},
\cite[\S2]{Rabinoff2014Witt}) how multiplication by $p$ interacts with these
operators.

\begin{prop}\label{prop:witt_multiplication_by_p}
Let $A$ be an $\F_p$-algebra. Then:
\begin{enumerate}
    \item $t$ is a natural ring homomorphism commuting with $F$, and its kernel is
    \[
    \ker\bigl(t \colon W_r(A) \to W_{r-1}(A)\bigr)
    \;=\; V^{r-1} A \;=\; \{(0, \dots, 0, c) : c \in A\}.
    \]
    \item $V$ is additive, and $F V = V F$.
    \item Multiplication by $p$ on $W_r(A)$ equals $V \circ F = F \circ V$
    (composed with the appropriate truncation); explicitly,
    \[
    p \cdot (a_0, \dots, a_{r-1}) \;=\; (0,\, a_0^p,\, \dots,\, a_{r-2}^p).
    \]
    Iterating, $p^j \cdot \vec a = (0, \dots, 0, a_0^{p^j}, \dots, a_{r-1-j}^{p^j})$;
    in particular $p^r = 0$ on $W_r(A)$, and
    \begin{equation}\label{eq:witt_p_to_r_minus_1}
    p^{r-1} \cdot (a_0, \dots, a_{r-1}) \;=\; \bigl(0, \dots, 0,\, a_0^{p^{r-1}}\bigr).
    \end{equation}
\end{enumerate}
\end{prop}

\begin{proof}
(1) That $t$ is a ring homomorphism follows from the recursive definition of the
$S_n, P_n$: the first $r-1$ components of a sum or product depend only on the first
$r-1$ components of the arguments (\Cref{prop:witt_addition_shape}). Naturality and
the commutation with the (componentwise) $F$ are clear, and the kernel is computed
componentwise. (2) Additivity of $V$ follows from \Cref{lemma:ghost_principle} and
the ghost identity $w_n(V\vec a) = p\, w_{n-1}(\vec a)$ (with $w_{-1} := 0$); the
commutation $FV = VF$ is immediate since $F$ is componentwise. (3) The identity
$F V = p$ holds over arbitrary rings for the general Frobenius, by
\Cref{lemma:ghost_principle} applied to
$w_n(FV\vec a) = w_{n+1}(V \vec a) = p\, w_n(\vec a) = w_n(p \vec a)$; in
characteristic $p$ the general Frobenius is componentwise, giving the displayed
formula. See \cite[II, \S6, Proposition~8 ff.]{serreLF} for details.
\end{proof}

\begin{example}\label{example:witt_of_Fp}
$W_r(\F_p) \cong \Z/p^r\Z$ canonically. Indeed, by
\Cref{eq:witt_p_to_r_minus_1} the unit $\underline 1 = (1, 0, \dots, 0)$ satisfies
$p^j \cdot \underline 1 = (0, \dots, 0, 1, 0, \dots, 0)$ ($1$ in position $j$), so
$\underline 1$ has additive order $p^r$; since $|W_r(\F_p)| = p^r$, the additive group
is cyclic of order $p^r$ generated by the unit, and $m \mapsto m \cdot \underline 1$
is a ring isomorphism $\Z/p^r\Z \xrightarrow{\;\cong\;} W_r(\F_p)$. We write
$\underline m \in W_r(\F_p)$ for the image of $m \in \Z/p^r\Z$. (Similarly, the full
ring of Witt vectors satisfies $W(\F_p) \cong \Z_p$; we shall not need this.)
\end{example}

\input{witt/WittVectorPrerequisites.tex}

\section{Weighted Witt addition in the cyclic calculation}

The following homogeneity property of the universal addition polynomials is what
makes degree estimates on Witt sums possible: even though the carry polynomials $C_n$
of \Cref{eq:witt_addition_shape} are complicated, they are \emph{isobaric} for the
weighting in which the $j$-th component has weight $p^j$.

\begin{lemma}[isobaricity of Witt addition]\label{lemma:witt_addition_isobaric}
Assign to the variables $X_j$ and $Y_j$ the weight $p^j$. Then the $n$-th addition
polynomial $S_n$ is isobaric of weight $p^n$: every monomial of $S_n$ has total weight
exactly $p^n$. The same holds for each component of a $d$-fold iterated Witt sum
$\bigoplus_{i=1}^{d} \vec a_i$, viewed as a universal polynomial in the components
$a_{i,j}$ of weight $p^j$.
\end{lemma}

\begin{proof}
The $n$-th ghost polynomial $w_n = \sum_{j \le n} p^j X_j^{p^{n-j}}$ is isobaric of
weight $p^n$ for this weighting. The recursion
\[
p^n S_n = \sum_{j \le n} p^j \bigl(X_j^{p^{n-j}} + Y_j^{p^{n-j}}\bigr)
- \sum_{j < n} p^j S_j^{p^{n-j}}
\]
preserves isobaricity of weight $p^n$ by induction on $n$: each $S_j$ is isobaric of
weight $p^j$, so $S_j^{p^{n-j}}$ is isobaric of weight $p^n$. Isobaricity persists
under iterated substitution of Witt sums into Witt sums (substituting an isobaric
polynomial of weight $p^j$ for a variable of weight $p^j$ preserves weights), giving
the statement for $d$-fold sums.
\end{proof}
