\documentclass[11pt]{article}

\usepackage[T1]{fontenc}
\usepackage[margin=1.08in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{xcolor}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=teal,urlcolor=magenta]{hyperref}

\newtheorem{lemma}{Lemma}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}

\newcommand{\A}{\mathbb A}
\newcommand{\Pj}{\mathbb P}
\newcommand{\F}{\mathcal F}
\newcommand{\Pic}{\operatorname{Pic}}

\title{Proposed Tendler-Style Replacement\\for Extension Across the Boundary}
\author{Standalone preview --- not incorporated into Chapter~3}
\date{July 2026}

\begin{document}

\maketitle

\noindent
This document is a preview of the proposed replacement only.  It makes no
change to the existing text of Chapter~3.

\section*{Proposed introductory description}

Second, on the geometric generic Abel--Jacobi fiber, the boundary is the
hyperplane at infinity.  A Tendler-style prime-to-$p$ power argument,
together with the structure of the abelian fundamental group of affine
space, forces the corresponding boundary inertia representation to be
trivial.  Purity then extends $\F^{[d]}$ uniquely across the boundary.

\section*{Proposed replacement for the extension argument}

\begin{lemma}
The rank-one local system $\F^{[d]}$ on $U^{(d)}$, which is tame along the
boundary $H$, extends uniquely to a rank-one local system on
$\widetilde C^{(d)}$.
\end{lemma}

\begin{proof}
Let $\xi$ be the generic point of $\Pic^{d}_{\widetilde C}$, let
$\Omega=k(\xi)^{\mathrm{sep}}$, and consider the geometric generic fiber of
the Abel--Jacobi morphism.  By the projective-bundle description,
\[
    \widetilde C^{(d)}_{\Omega}\simeq \Pj^{r}_{\Omega},
    \qquad
    H_{\Omega}\simeq \Pj^{r-1}_{\Omega},
\]
and hence
\[
    U^{(d)}_{\Omega}
      =\widetilde C^{(d)}_{\Omega}\setminus H_{\Omega}
      \simeq \A^{r}_{\Omega}.
\]

Let
\[
    \chi\colon
    \pi_{1}\bigl(\A^{r}_{\Omega}\bigr)
       \longrightarrow \Lambda^{\times}
\]
be the character corresponding to the restriction of $\F^{[d]}$ to this
fiber.

If $\operatorname{char}(k)=0$, then
\[
    \pi_{1}\bigl(\A^{r}_{\Omega}\bigr)=1,
\]
so $\chi$ is trivial \cite[Example~4.14]{Tendler}.

Suppose now that $\operatorname{char}(k)=p>0$.  Let $I_{\infty}$ denote the
inertia group at the generic point of the hyperplane at infinity.  Since
$\F^{[d]}$ is tame along $H$, the finite group $\chi(I_{\infty})$ has order
prime to $p$.  Let $N$ be its exponent.  Then $(N,p)=1$, and the character
$\chi^{N}$ is trivial on $I_{\infty}$.

Consequently, the local system corresponding to $\chi^{N}$ is unramified at
the generic point of $\Pj^{r-1}_{\Omega}$.  By purity, it extends to
$\Pj^{r}_{\Omega}$.  Since
\[
    \pi_{1}\bigl(\Pj^{r}_{\Omega}\bigr)=1,
\]
this extension is constant, and therefore
\[
    \chi^{N}=1.
\]

On the other hand, $\chi$ factors through
\[
    \pi_{1}\bigl(\A^{r}_{\Omega}\bigr)^{\mathrm{ab}},
\]
which is a pro-$p$ group \cite[Example~4.15]{Tendler}.  Hence the finite group
$\operatorname{im}(\chi)$ is a $p$-group.  Since its exponent divides $N$,
and $N$ is prime to $p$, it follows that
\[
    \operatorname{im}(\chi)=1.
\]
Thus $\chi$ is trivial.

Let $\eta$ be the generic point of $H$.  The preceding argument shows that
the pullback of the finite inertia representation at $\eta$ to the geometric
generic fiber is trivial.  The corresponding extension of henselian discrete
valuation rings has ramification index $1$ and separable residue-field
extension.  Triviality of a finite inertia representation is detected after
such a base change.  Hence the inertia group at $\eta$ acts trivially on
$\F^{[d]}$.

Therefore $\F^{[d]}$ is unramified at the generic point of $H$.  Since
$\widetilde C^{(d)}$ is regular and $H$ is the only codimension-one component
of $\widetilde C^{(d)}\setminus U^{(d)}$, purity gives an extension of
$\F^{[d]}$ to $\widetilde C^{(d)}$.  The extension is unique because
\[
    \pi_{1}\bigl(U^{(d)}\bigr)
       \longrightarrow
    \pi_{1}\bigl(\widetilde C^{(d)}\bigr)
\]
is surjective.
\end{proof}

\begin{remark}
The argument does not assert that tame ramification is generally
unramified.  Tameness is used only to choose $N$ prime to $p$.  The conclusion
that the inertia character is trivial then follows from the global geometry
of the geometric generic fiber and from the fact that the abelian fundamental
group of affine space is pro-$p$.
\end{remark}

\begin{thebibliography}{9}

\bibitem{Tendler}
Avichai Tendler,
\emph{Geometric Class Field Theory},
Master's thesis, Hebrew University of Jerusalem, 2010;
arXiv:1507.00104 (2015), especially Examples~4.14--4.15 and \S9.3.
\url{https://arxiv.org/abs/1507.00104}.

\end{thebibliography}

\end{document}
