This chapter collects the constructions and conventions used in both main parts of
the thesis. Rank-one \'etale local systems are the natural objects in the statement
of geometric class field theory. For the geometric and ramification-theoretic
arguments, however, it is more convenient to work with torsors: they are represented
by finite \'etale covers, admit concrete contracted products and quotients, and make
ramification accessible through extensions of local fields.

If \(\Lambda\) is a finite commutative ring and \(G=\Lambda^\times\), the sheaf of
frames of a rank-one \(\Lambda\)-local system is a \(G\)-torsor, and conversely a
\(G\)-torsor determines an associated rank-one local system. We establish this
dictionary below and record its compatibility with pullback, tensor products,
symmetric powers, and ramification. Thus, the main results will be stated in the
language of local systems, while the constructions and ramification calculations
will generally be carried out in the language of torsors.

\section{Torsors and Rank-One Local Systems}
% $X$ with etale site, but say things here work for toposes in general and flat sites in general.

In what follows, we largely adhere to the treatment of torsors and group objects found in published notes of Alex Youcis \cite{YoucisTorsors}.
Let $\sC=(\cC, J)$ be a site and let $\cE=Sh(\sC)$ be the associated topos. 
Let $\mathcal{G}$ be a group object in $\mathcal{E}$. 
We denote by $\mathcal{G}\mathcal{E}$ the category of objects in $\mathcal{E}$ endowed with a left $\mathcal{G}$-action. 

\begin{definition}
    A \textbf{$\mathcal{G}$-torsor} in $\mathcal{E}$ is an object $\mathcal{P}$ of $\mathcal{G}\mathcal{E}$ satisfying the following conditions:
    \begin{enumerate}
        \item The structural morphism $\mathcal{P} \to 1$ is an epimorphism in $\mathcal{E}$ (i.e., $\mathcal{P}$ is locally non-empty).
        \item The map $\mathcal{G} \times \mathcal{P} \to \mathcal{P} \times \mathcal{P}$ defined by $(g, p) \mapsto (g \cdot p, p)$ is an isomorphism in $\mathcal{E}$ (i.e., $\mathcal{G}$ acts simply transitively on $\mathcal{P}$).
    \end{enumerate}
\end{definition}

Since $\mathcal{E}$ is the topos of sheaves on a site $\sC$, the definition can be reformulated in terms of covers. A $\mathcal{G}$-sheaf $\mathcal{P}$ is a $\mathcal{G}$-torsor if:
\begin{enumerate}
    \item For every object $X \in \mathcal{C}$, there exists a covering $\{ U_i \to X \} \in J$ such that $\mathcal{P}(U_i) \neq \emptyset$ for all $i$.
    \item For any $X \in \mathcal{C}$ where $\mathcal{P}(X)$ is non-empty, the action of $\mathcal{G}(X)$ on $\mathcal{P}(X)$ is simply transitively.
\end{enumerate}

A fundamental property of torsors is their local triviality: 
a $\mathcal{G}$-sheaf $\mathcal{P}$ is a $\mathcal{G}$-torsor if and only if it is locally isomorphic to the trivial torsor. 
Specifically, for every $X \in \mathcal{C}$, there must exist a cover $\{ U_i \to X \}$ such that the restriction $\mathcal{P}|_{U_i}$ is 
isomorphic, as a $\mathcal{G}|_{U_i}$-sheaf, to $\mathcal{G}|_{U_i}$ acting on itself by left multiplication.

A \textbf{morphism of $\mathcal{G}$-torsors} $f: \mathcal{P}_1 \to \mathcal{P}_2$ is a morphism of sheaves that is equivariant with respect to the $\mathcal{G}$-action.

\begin{prop}\label{prop:torsor_morphism_iso}
    Every morphism of $\mathcal{G}$-torsors is an isomorphism.
    Consequently, the category of $\mathcal{G}$-torsors in $\mathcal{E}$ forms a groupoid.
\end{prop}
\begin{proof}
    Locally on a cover trivializing both torsors, such a morphism is a $\mathcal{G}$-equivariant endomorphism
    of the trivial torsor $\mathcal{G}$, i.e.\ right translation by a section of $\mathcal{G}$, hence an
    isomorphism; and being an isomorphism may be checked on a cover.
\end{proof}

\begin{definition}
    We denote the groupoid of $\mathcal{G}$-torsors in $\mathcal{E}$ by $\mathbf{Tors}(\mathcal{E}, \mathcal{G})$ .  The set of isomorphism classes of $\mathcal{G}$-torsors is denoted by $\mathrm{Tors}(\mathcal{E}, \mathcal{G})$.
\end{definition}

Torsors exhibit functoriality with respect to the group object:

\begin{definition}
Let $\varphi: \mathcal{G}_1 \to \mathcal{G}_2$ be a morphism of group 
sheaves on $\sC$, and let $\mathcal{P}$ be a $\mathcal{G}_1$-torsor. We define the \textbf{contracted product} $\mathcal{G}_2 \times^{\mathcal{G}_1} \mathcal{P}$ as the quotient sheaf $\mathcal{G}_1 \backslash (\mathcal{G}_2 \times \mathcal{P})$, where $\mathcal{G}_1$ acts on the product by:
\[ g_1 \cdot (g_2, p) = (g_2 \varphi(g_1)^{-1}, g_1 \cdot p) \]

The contracted product inherits a natural left $\mathcal{G}_2$-action given on local sections by $h \cdot [g_2, p] = [h g_2, p]$, which endows it with the structure of a $\mathcal{G}_2$-torsor. 
\end{definition}

This construction yields a functor:
\[ \varphi_*: \mathbf{Tors}(\cE, \mathcal{G}_1) \to \mathbf{Tors}(\cE, \mathcal{G}_2), \quad \mathcal{P} \mapsto \mathcal{G}_2 \times^{\mathcal{G}_1} \mathcal{P} \]
On the level of isomorphism classes, $\varphi_*$ induces a map of pointed sets $\mathrm{Tors}(\cE, \mathcal{G}_1) \to \mathrm{Tors}(\cE, \mathcal{G}_2)$, sending the class of the trivial $\mathcal{G}_1$-torsor to the class of the trivial $\mathcal{G}_2$-torsor.

When $\mathcal{G}$ is a \textbf{sheaf of abelian groups} (an \textit{abelian sheaf}), the pointed set $\mathrm{Tors}(\cE, \mathcal{G})$ 
inherits the structure of an abelian group:
\begin{definition}
    Assume $\mathcal{G}$ is abelian sheaf. Let $\mathcal{P}_1$ and $\mathcal{P}_2$ be objects of $\mathbf{Tors}(\cE, \mathcal{G})$. 
    We define the \textbf{product} $\mathcal{P}_1 \otimes^{\cG} \mathcal{P}_2$ to be the quotient sheaf 
    $(\mathcal{P}_1 \times \mathcal{P}_2)/\mathcal{G}$, where $\mathcal{G}$ acts on $T$-points by having:
    \[ g \cdot (f_1, f_2) := (g f_1, g^{-1} f_2) \]
    The group object $\mathcal{G}$ then acts on the resulting quotient via its action on the presheaf quotient, which is given on classes by:
    \[ g \cdot [(f_1, f_2)] = [(g f_1, f_2)] = [(f_1, g f_2)] \]
    where the square brackets denote the class in the quotient set.\footnote{
    Equivantly, the sum is obtained as the contracted product of the $\cG \times \cG$-torsor $\cP_1 \times \cP_2$ along the multiplication map
$m: \cG \times \cG \to \cG$. }
\end{definition}

Let $[\mathcal{P}_1]$ and $[\mathcal{P}_2]$ be the isomorphism classes of $\mathcal{P}_1$ and $\mathcal{P}_2$ in $\mathrm{Tors}(\cE, \mathcal{G})$.
We define the sum $[\mathcal{P}_1] + [\mathcal{P}_2]$ to be the class $[\cP_1 \otimes^{\cG} \cP_2]$.
This structure turns $\mathrm{Tors}(\cE, \mathcal{G})$ into an abelian group, 
where the identity is the class of the trivial torsor and the inverse is obtained by the opposite action.

We now record the dictionary that explains the role of torsors in this thesis.
Let $\Lambda$ be a commutative ring object of $\mathcal{E}$ and let
$G=\Lambda^\times$ be its group of units. We write
$\mathbf{Pic}(\mathcal{E},\Lambda)$ for the groupoid of locally free
$\Lambda$-modules of rank one. For $\mathcal{L}$ in this groupoid, its
\textbf{frame torsor} is
\[
\operatorname{Fr}(\mathcal{L})
  :=\underline{\operatorname{Isom}}_\Lambda(\Lambda,\mathcal{L}).
\]
The group $G$ acts on frames by precomposition with multiplication on $\Lambda$.
Conversely, if $\mathcal{P}$ is a $G$-torsor, its \textbf{associated
$\Lambda$-module} is the contracted product
\[
\mathcal{P}\times^G\Lambda
  :=(\mathcal{P}\times\Lambda)/G,
\qquad
g\cdot(p,\lambda)=(gp,g^{-1}\lambda),
\]
where $G$ acts on $\Lambda$ by multiplication.

\begin{prop}[The torsor--local-system dictionary]
\label{prop:torsor_module_equivalence}
The functors
\[
\mathcal{P}\longmapsto\mathcal{P}\times^G\Lambda,
\qquad
\mathcal{L}\longmapsto\operatorname{Fr}(\mathcal{L})
\]
are mutually quasi-inverse symmetric monoidal equivalences
\[
(\mathbf{Tors}(\mathcal{E},G),\otimes^G,G)
\xrightarrow{\ \sim\ }
(\mathbf{Pic}(\mathcal{E},\Lambda),\otimes_\Lambda,\Lambda).
\]
These equivalences commute with pullback.
\end{prop}

\begin{proof}
Both assertions may be checked locally. On a cover on which $\mathcal{P}$ is
the trivial torsor $G$, the associated module
$\mathcal{P}\times^G\Lambda$ identifies with $\Lambda$. Conversely, on a
cover on which $\mathcal{L}$ is free of rank one,
$\operatorname{Fr}(\mathcal{L})$ identifies with $G$ acting on itself by
translation. These local identifications are compatible with the descent
data and give the two quasi-inverse equivalences. Applying the same argument
to products of local trivializations identifies contracted products with
tensor products. The construction is defined by fiber products and sheaf
quotients, and therefore commutes with pullback.
\end{proof}

When $\mathcal{E}=\operatorname{Sh}(X_{\text{\'et}})$ and $\Lambda$
is a finite constant ring, the objects of
$\mathbf{Pic}(\mathcal{E},\Lambda)$ are precisely the rank-one
$\Lambda$-local systems on $X$. We retain local-system language in the
statements of the main theorems and use the equivalent torsor language for
the geometric constructions and ramification calculations. We will pass
between the two languages using \Cref{prop:torsor_module_equivalence}.

Lastly, for any object $\cX \in \mathcal{E}$, there is a canonical identification between the slice category
$(\mathcal{G}\mathcal{E})/\cX$ and the category of group objects $\mathcal{G}(\mathcal{E}/\cX)$, where $\cX$ is viewed as having the 
trivial $\mathcal{G}$-action.

We denote by $\mathbf{Tors}(\cX, \cG)$ the category of $G$-torsors over $\cX$ in $\cG \cE_{/\cX}$.

%%% %%% %%% %%% %%% %%% %%% %%%
%       Torsors as Spaces
%%% %%% %%% %%% %%% %%% %%% %%%
\section{Torsors on the \'Etale Sites}
Fix a scheme $X$, and let $G$ be a smooth affine $X$-group scheme. 
Denote by $X_{\text{Ét}}$ and $X_{\text{ét}}$ the big and small étale sites on $X$, respectively. 
The functor of points of $G$, which we denote by $G(\cdot) = \mathrm{Hom}_X(-, G)$, defines a group sheaf on 
$X_{\text{ét}}$.

\begin{definition} A \textit{principal $G$-bundle} (or \textit{principal homogeneous space}) for $G$ is a 
scheme $f : Y \to X$ equipped with a left $G$-action $\rho: G \times_X Y \to Y$ satisfying:
\begin{enumerate}
    \item The morphism $G \times_X Y \to Y \times_X Y$ sending $(g, y) \mapsto (gy, y)$ is an isomorphism of $X$-schemes.
    \item There exists an étale covering $\{U_i \to X\}$ such that $Y_{U_i} \cong G_{U_i}$ as $G$-schemes, 
    where $G$ acts on itself by left translation.
\end{enumerate}
\end{definition}

\begin{rem*}
    Since $G \to X$ is smooth and $Y$ is étale-locally isomorphic to $G$, 
    the morphism $f: Y \to X$ is smooth and affine. Note that $Y$ is generally not étale over $X$ unless $G$ is an 
    étale group scheme (e.g., a finite constant group).
    Similarly, if $G$ is finite then $Y \to X$ is finite.
\end{rem*}

Similarly to the case of $G$-torsors of a topos, we define a morphism of principal $G$-bundles to be a morphism of $X$-schemes commuting with the
$G$-action. We now have:

\begin{theorem}\label{theorem:torsors_are_realized_as_spaces}
    The morphism sending $Y \mapsto \mathrm{Hom}_X(-, Y)$ is an equivalence of categories from the category of principal $G$-bundles 
    to the category of $G$-torsors on $X_{\text{\'Et}}$
    Similarly, the morphism sending $Y$ to $\mathrm{Hom}_X(-, Y)$ to the category of $G$-torsors on $X_{\text{ét}}$ is an equivalence.
\end{theorem}

%% [REVIEW: unlabeled & never cited -- the big/small-site comparison is used implicitly whenever torsors are realized as schemes; consider labeling it and citing it (e.g. line ~381), or merging into the theorem above]
\begin{cor}
    There is a natural equivalence $\mathbf{Tors}(X_{\mathrm{\text{\'et}}}, G) \cong \mathbf{Tors}(X_{\text{\'Et}}, G)$ 
    inducing a bijection of pointed sets $\mathrm{Tors}(X_{\text{\'et}}, G) \xrightarrow{\cong} \mathrm{Tors}(X_{\text{\'Et}}, G)$ 
    which is an isomorphism of abelian groups if $G$ is abelian.
    And every $G$-torsor, in each of the above sites can be realized as a scheme, which is a prinicipal $G$-bundle.
\end{cor}

%%% %%% %%% %%% %%% %%% %%% %%%
%       Torsors and Cohomology
%%% %%% %%% %%% %%% %%% %%% %%%

% \subsection*{Torsors and Cohomology}
% We qoute without proof:
% \begin{theorem}
% There is a natural bijection of pointed sets     
% $\text{Tors}(\mathcal{G|_T}) \to \check{H}^1(T, \mathcal{G})$. Moreover, if $\mathcal{G}$ is an abelian group sheaf, it's an isomorphism of abelian groups.
% \end{theorem}

% The idea is that for every $[\mathcal{P}] \in \text{Tors}(T, \mathcal{G})$ 
% We 
% \begin{enumerate}
%     \item Choose a covering $\{U_i \to T\}$ such that $\mathcal{P}(U_i) \neq \emptyset$ for all $i$
%     \item choose sections $\alpha_i \in \mathcal{F}(U_i)$
% \end{enumerate}

% Then we note that for all $(i,j)$ the elements $\alpha_i |_{U_i \times_X U_j}$ and $\alpha_j |_{U_i \times_X U_j}$ differ by a unique element of $\mathcal{G}(U_{ij})$
% there exists a unique $s_{ij} \in \mathcal{G}(U_{ij})$ such that $\alpha_i |_{U_i \times_X U_j} = s_{ij}(\alpha_j |_{U_i \times_X U_j})$. 
% One can then easily see that $(s_{ij})$ defines an element of  $\check{H}^1(T, \mathcal{G})$
% which is independent of the choice of repreantiative $\cP$, choice of covering $\{U_i \to T\}$ and choice of sections.



%%% %%% %%% %%% %%% %%% %%% %%%
%       Constant Finite Group Torsors
%%% %%% %%% %%% %%% %%% %%% %%%

\subsection*{Constant Finite Group Torsors}

Let $G$ be a finite group, within this section, we denote the associated constant group scheme over $X$ by $\underline{G}$ to maintain a clear distinction between the group as a set and the group as a scheme. In subsequent sections, we shall follow the standard practice of identifying $G$ with its constant group scheme and omit the underline for brevity.

$\underline{G}$ is given by $\coprod_{g \in G} X$ with the action shuffeling the $X$'s according to multiplication.

By following the definitions, one sees that if $X$ be a connected scheme and $f : Y \to X$ is a finite Galois cover with Galois group $G$. 
Then, $f : Y \to X$ is a principal $\underline{G}$-bundle.
(Recall that a \textit{finite Galois cover} is a finite étale surjection $Y \to X$ with $Y$ connected and such that 
$G = \text{Aut}(Y/X)$ acts transitively on the geometric points of $Y$ lying over any geometric point of $X$).

On the otherhand if $f: Y \to X$ is a principal $\underline{G}$-bundle with $Y$ connected, then $Y$ is a finite Galois cover with
automorphism group $G$.

However, not all $\underline{G}$-torsors are connected. If $H\subset G$ is a proper subgroup then any connected finite \'etale cover $f: Y \to X$ with 
Galois group $H$ gives rise to a non-connected $\underline{G}$-torsor by looking at the induced $\underline{G}$-torsor $\varphi_*(Y)$ under the inclusion $\varphi: \underline{H} \to \underline{G}$.
On the otherhand, if we fix a geometric point $\overline{x} \to X$, then to give an homomorphism
$\rho \in \mathrm{Hom}_{\mathrm{cont}}(\pi_1^{\mathrm{et}}(X, x), G)$ is equivilant to give a connected pointed Galois cover
$(Y, \overline{y}) \to (X, \overline{x})$ with Galois group $H=\rho(\pi_1^{\mathrm{et}}(X, x)) \subset G$. 
Thus, pushing forward to $\underline{G}$ we get a prinicipal $\underline{G}$-bundle. The choice of a different geometric point $\overline{x'} \to X$
differ the homomorphism by an inner automorphism, thus we have:

\begin{theorem}\label{theorem:equivalence_fundamental_covers}
    Let $X$ be a connected scheme and $\overline{x}$ a geometric point of $X$. Suppose in addition that $G$ is a finite abstract group. 
    Define a map
    \begin{equation}
        \mathrm{Hom}_{\mathrm{cont}}(\pi_1^{\mathrm{et}}(X, \overline{x}), G) / \mathrm{Inn}(G) \to \mathrm{Tors}(X_{\text{\'Et}}, \underline{G}) 
    \end{equation}
by sending a homomorphism $\rho : \pi_1^{\mathrm{et}}(X, \overline{x}) \to G$ 
to the principal $\underline{G}$-bundle $\varphi_*(Y)$ where $Y$ is the principal $\underline{\rho(\pi_1^{\mathrm{et}}(X, \overline{x}))}$-bundle 
obtained above and $\varphi$ is the inclusion $\rho(\pi_1^{\mathrm{et}}(X, \overline{x})) \hookrightarrow G$. Then, the map 
 is a bijection of pointed sets where the trivial homomorphisms
  (which is the only element of its $\mathrm{Inn}(G)$-orbit) is the distinguished element of the left hand side.
\end{theorem}

If $G$ is abelian then $\mathrm{Inn}(G)$ is trivial, and we obtain:
\begin{cor}\label{cor:abelian_equivilance_fundamental_torsors}
    Let $G$ be a finite abelian group, $X$ a connected scheme, and $\overline{x}$ a geometric point of $X$. Then, the map from \Cref{theorem:equivalence_fundamental_covers}
     induces an isomorphism of abelian groups
    \begin{equation}
        \mathrm{Hom}_{\mathrm{cont.}}(\pi_1^{\text{ét}}(X, \overline{x}), G) \xrightarrow{\cong} \Tors(X_{\text{\'Et}}, \underline{G})
    \end{equation}
\end{cor}

For $G=\Lambda^\times$, the character in
\Cref{cor:abelian_equivilance_fundamental_torsors} is also the monodromy
character of the associated rank-one $\Lambda$-local system. In particular,
the torsor and the local system have the same restrictions to inertia and to
the upper ramification groups. Thus, one has ramification bounded by a given
modulus, or is tamely ramified along a given divisor, if and only if the other
does.

\subsection*{Decomposition of Torsors}
\textcolor{red}{because the contracted product is also P/H, we should add this!!! say this. etc... maybe have a section about qoutient of schemes.}
In the case of finite groups, the functoriality of the contracted product has a concrete geometric interpretation as a tower of covers. Let $G$ be a finite abelian group and $H \subseteq G$ a subgroup. 
Let $\pi: G \to G/H$ be the natural quotient map.

\begin{prop}\label{prop:quotient_torsors_finite}\label{prop:quotient_torsors}
    Let $\mathcal{P} \to X$ be a $G$-torsor in $X_{\text{ét}}$. 
    There exists a factorization of the morphism $\mathcal{P} \to X$:
    \[ \mathcal{P} \xrightarrow{\phi} \mathcal{P}_{G/H} \xrightarrow{\psi} X \]
    that is unique up to a unique isomorphism commuting with the projections, where:
    \begin{enumerate}
        \item $\mathcal{P}_{G/H} := \mathcal{P} \times^G (G/H)$ is a $G/H$-torsor over $X$.
        \item $\mathcal{P}$ is an $H$-torsor over the scheme $\mathcal{P}_{G/H}$.
    \end{enumerate}
\end{prop}

\begin{proof}
    The first assertion follows directly from the definition of the contracted product functor $\pi_*: \mathbf{Tors}(X, G) \to \mathbf{Tors}(X, G/H)$. To see the second assertion, we note that the map $\phi: \mathcal{P} \to \mathcal{P}_{G/H}$ is surjective. Locally on $X$, we may choose a cover $U \to X$ such that $\mathcal{P}|_U \cong G \times U$. 
    Over this cover, the map $\phi$ is identified with the product of the quotient map and the identity:
    \[ \pi \times \text{id}_U: G \times U \to (G/H) \times U \]
    Since $G \to G/H$ is a trivial $H$-torsor (the fiber over any element $\bar{g} \in G/H$ is a coset $gH$, which is an $H$-set isomorphic to $H$ acting on itself), $\mathcal{P}$ is locally an $H$-torsor over $\mathcal{P}_{G/H}$. By the descent of torsors, $\mathcal{P}$ is an $H$-torsor over $\mathcal{P}_{G/H}$ globally.

    For uniqueness, suppose $\mathcal{P} \to \mathcal{Q} \to X$ is another such factorization. Because $\mathcal{P} \to \mathcal{Q}$ is an $H$-torsor, $\mathcal{Q}$ represents the categorical quotient $\mathcal{P}/H$ in $X_{\text{ét}}$. Since $\mathcal{P}_{G/H}$ also represents this quotient, the universal property of quotients yields a unique isomorphism $\mathcal{Q} \xrightarrow{\sim} \mathcal{P}_{G/H}$ making all associated diagrams commute.

\end{proof}
%\textcolor{red}{Let us give a final note that, evidently, $\mathrm{Aut}(G)$ acts on $\mathrm{Hom}_{\mathrm{cont.}}(\pi_1^{\text{ét}}(X, x), G)$ on the right, and if we consider the quotient $\mathrm{Hom}_{\mathrm{cont.}}(\pi_1^{\text{ét}}(X, x), G)/\mathrm{Aut}(G)$ we get the pointed set of all connected finite Galois covers of $X$ with Galois group isomorphism to a subgroup of $G$.}

%%% %%% %%% %%% %%% %%% %%% %%% %%% %%% %%% %%% %%% %%% %%% %%%
%       Qoutient of G-torsors
%%% %%% %%% %%% %%% %%% %%% %%% %%% %%% %%% %%% %%% %%% %%% %%%

% \subsection*{Qoutients of \texorpdfstring{$G$}{G}-Torsors}
% Let $G$ be a finite abelian group, and let $H \subseteq G$ be a subgroup. 
%  Consider the natural quotient homomorphism $\pi: G \to G/H$. Given a $G$-torsor $\mathcal{P} \to X$ (in the fppf or étale topology), we may associate to it a $G/H$-torsor, 
%  denoted by $\pi_*(\mathcal{P})$ or $\mathcal{P}^{G/H}$, via the extension of scalars.
%  The object $\mathcal{P}^{G/H}$ is defined as the contracted product:
%  $$\mathcal{P}^{G/H} = \mathcal{P} \otimes^G (G/H)$$
%  Recall that $\mathcal{P}^{G/H}$ is the quotient of the product $\mathcal{P} \times (G/H)$ by the $G$-action defined by 
%  $g \cdot (p, \bar{g}') = (g \cdot p, \pi(g^{-1})\bar{g}')$. 
%  Consequently, we have a canonical morphism of sheaves 
%  $\phi: \mathcal{P} \to \mathcal{P}^{G/H}$ which, on local sections, acts by 
%  $p \mapsto [p, \bar{e}]$, where $\bar{e}$ is the identity element in $G/H$. 
%  To see that $\mathcal{P}$ carries the structure of an $H$-torsor over $\mathcal{P}^{G/H}$, 
%  consider a local trivializing cover $\{U_i \to X\}$ for $\mathcal{P}$ as a $G$-torsor. 
%  Over each $U_i$, we have an isomorphism $\mathcal{P}|_{U_i} \cong G_{U_i}$. 
%  Under this isomorphism, the contracted product locally satisfies:
%  $$(\mathcal{P} \otimes^G G/H)|_{U_i} \cong (G \otimes^G G/H)_{U_i} \cong (G/H)_{U_i}$$
%  Explicitly, the local identification $(g, \bar{g}') \sim (e, \pi(g)\bar{g}')$ 
%  shows that every equivalence class in the fiber has a unique representative of the form 
%  $[e, \bar{g}]$. 
%  The map $\phi$ locally corresponds to the quotient map $G \to G/H$. 
%  Since the kernel of this map is $H$, and $G$ is a trivial $H$-torsor over $G/H$, 
%  it follows by descent that $\mathcal{P}$ is an $H$-torsor over $\mathcal{P}^{G/H}$.
%  We summarize this construction in the following proposition:
%  \begin{prop}\label{prop:quotient_torsors}
%     Let $G$ be an abelian group and $H \subset G$ a subgroup. 
%     Any $G$-torsor $\mathcal{P} \to X$ admits a natural factorization:
%     $$\mathcal{P} \xrightarrow{} \mathcal{P}^{G/H} \xrightarrow{} X$$
%     where $\mathcal{P}^{G/H} \to X$ is a $G/H$-torsor and $\mathcal{P} \to \mathcal{P}^{G/H}$ is an $H$-torsor.
% \end{prop}

\section{Symmetric Powers of Schemes and Torsors}
This section reviews the construction of quotients for schemes and torsors under finite group actions, specifically focusing on symmetric powers. 
To ensure these quotients exist as schemes, we utilize the framework of admissible actions from \cite{sga1}. 
Our treatment here closely follows the exposition in \cite{Guignard2018}
The definitions and results presented below are adapted from their work, the difference being that we ask $\Gamma$ to act on the left, to make the later construction of symmetric powers more natural. 
This foundation provides the necessary criteria for admissibility and base change required to define the symmetric powers of a scheme $X$
 and a $G$-torsor $\mathcal{P}$ over $X$.


Let $S$ be a scheme.

\begin{definition}[(\cite{sga1}, V.1.7).]
    \noindent
    \begin{itemize}
        \item Let $T$ be an object of a category $\mathcal{C}$ endowed with a right action of a group $\Gamma$. We say that \textbf{the quotient $T/\Gamma$ exists} in $\mathcal{C}$ if the covariant functor
    \[
    \begin{aligned}
    \mathcal{C} &\to \text{Sets} \\
    U &\mapsto \text{Hom}_{\mathcal{C}}(T, U)^{\Gamma}
    \end{aligned}
    \]
    is representable by an object of $\mathcal{C}$.
    \item Let $T$ be an $S$-scheme. An action of a finite group $\Gamma$ on $T$ is \textbf{admissible} if there exists an affine $\Gamma$-invariant morphism $f : T \to T'$ such that the canonical morphism $\mathcal{O}_{T'} \to f_* \mathcal{O}_T$ induces an isomorphism from $\mathcal{O}_{T'}$ to $(f_* \mathcal{O}_T)^{\Gamma}$.
\end{itemize}
\end{definition}

%% [REVIEW: never cited -- admissibility facts are used only implicitly (e.g. 'admissible quotient' in cor:sym-power-quotient discussion); consider labeling + citing, or compressing into prose with the SGA1 citation]
\begin{prop}
    The following holds:
    \begin{enumerate}
        \item \textbf{(\cite{sga1} V.1.3)}. Let $T$ be an $S$-scheme endowed with an admissible right action of a finite group $\Gamma$. If $f : T \to T'$ is an affine $\Gamma$-invariant morphism such that the canonical morphism $\mathcal{O}_{T'} \to f_* \mathcal{O}_T$ induces an isomorphism from $\mathcal{O}_{T'}$ to $(f_* \mathcal{O}_T)^{\Gamma}$, then the quotient $T/\Gamma$ exists and is isomorphic to $T'$.
        \item \textbf{(\cite{sga1}, V.1.8)}. Let $T$ be an $S$-scheme endowed with a right action of a finite group $\Gamma$. Then, the action of $\Gamma$ on $T$ is admissible if and only if $T$ is covered by $\Gamma$-invariant affine open subsets.
        \item \textbf{(\cite{sga1}, V.1.9)}. Let $T$ be an $S$-scheme endowed with an admissible right action of a finite group $\Gamma$, and let $S'$ be a flat $S$-scheme. Then, the action of $\Gamma$ on the $S'$-scheme $T \times_S S'$ is admissible, and the canonical morphism
            \[
            (T \times_S S')/\Gamma \to (T/\Gamma) \times_S S'
            \]
            is an isomorphism.
    \end{enumerate}
\end{prop}



Now let $X$ be an $S$-scheme and let $d \geq 0$ be an integer. The group ${S}_d$ of permutations of $\llbracket 1, d \rrbracket$ acts on the right on the $S$-scheme $X^{\times_S d} = X \times_S \dots \times_S X$ by the formula
\[
(x_i)_{i \in \llbracket 1, d \rrbracket} \cdot \sigma = (x_{\sigma(i)})_{i \in \llbracket 1, d \rrbracket}.
\]

\begin{prop}[\cite{Guignard2018} Proposition 2.27]
    If $X$ is a scheme, Zariski locally quasi-projective over $S$, then the right action of the symmetric group $S_d$ on the $d$-fold fiber product 
    $X^{\times_S d}$ is admissible. 
    Consequently, the quotient $\mathrm{Sym}_S^d(X) = X^{\times_S d}/S_d$ exists as a scheme over $S$.
\end{prop}

\begin{definition}
    Under the hypotheses of the proposition above, we define the \textbf{relative symmetric product} of $X$ over $S$ 
    of degree $d$ as the quotient
    $$\mathrm{Sym}_S^d(X) \coloneqq X^{\times_S d}/S_d.$$
    When the base scheme $S$ is clear from the context, we shall denote this quotient by 
    $X^{(d)}$.
\end{definition}

Guingard shows that when $X=\Spec(B)$ and $S=\Spec(A)$ then $\Sym_{S}^d(X)$ is representable by an affine $S$-scheme (See \cite{Guignard2018} Remark 2.28).

\begin{prop}[\cite{Guignard2018} Proposition 2.28]\label{prop:symmetric_power_flat_base_change}
If $X$ is flat and Zariski-locally quasi-projective over $S$, then $\text{Sym}_S^d(X)$ is flat over $S$. Moreover, for any $S$-scheme $S'$, the canonical morphism
\[
\text{Sym}_{S'}^d(X \times_S S') \to \text{Sym}_S^d(X) \times_S S'
\]
is an isomorphism.
\end{prop}


\subsection*{Symmetric Powers of Torsors}
Let $G$ be a finite abelian group, let $\cP$ be a $G$-torsor over an $S$-scheme $X$ in $S_{\text{Ét}}$. 


%% [REVIEW: never cited -- presumably the input for prop:symmetric_power_torsor (Guignard 2.32), but no proof ever invokes it; cite it there or remove]
\begin{prop}[{[\cite{sga1}]}, IX.5.8]
Assume that $\cP$ and $X$ are endowed with right actions from a finite group $\Gamma$ 
such that the morphism $\cP \to X$ is $\Gamma$-equivariant, and that the following properties hold:
\begin{enumerate}
    \item[(a)] The right $\Gamma$-action on $\cP$ commutes with the left $G$-action.
    \item[(b)] The right $\Gamma$-action on $X$ is admissible, and the quotient morphism $X \to X/\Gamma$ is finite.
    \item[(c)] For any geometric point $\bar{x}$ of $X$, the action of the stabilizer $\Gamma_{\bar{x}}$ of $\bar{x}$ in $\Gamma$ on the fiber $\cP_{\bar{x}}$ of $\cP$ at $\bar{x}$ is trivial.
\end{enumerate}
Then the action of $\Gamma$ on $\cP$ is admissible, and $\cP/\Gamma$ is a $G$-torsor over $X/\Gamma$ in $S_{\text{Ét}}$.
\end{prop}

By \Cref{theorem:torsors_are_realized_as_spaces}, $\cP$ is representable by a finite étale $X$-scheme.
For each $i \in  \llbracket 1, d \rrbracket$ let $p_i : X^{\times_S d} \to X$ be the projection on $i$-th factor, and let us consider the $G$-torsor
\[
p_1^{-1}\cP \otimes^G \cdots \otimes^G p_d^{-1}\cP = \KG \backslash \cP^{\times_S d}
\]
over $X^{\times_S d}$, where $\KG \subseteq G^d$ is the kernel of the multiplication morphism $G^d \to G$ (the dependence on $d$ is suppressed in the notation).
\footnote{
    Equivantly, the sum is obtained as the contracted product of the $G^d$-torsor $p_1^{-1}\cP_1 \times \dots \times p_d^{-1}\cP_d$ along the multiplication map
$m: G^d \to G$. }
The object $\KG \backslash \cP^{\times_S d}$ of $S_{\text{Ét}}$ is too representable by an $S$-scheme which is finite étale over $X^{\times_S d}$.
The group ${S}_d$ acts on the right on $\KG \backslash \cP^{\times_S d}$ by the formula
\[
(p_i)_{i \in \llbracket 1, d \rrbracket} \cdot \sigma = (p_{\sigma(i)})_{i \in \llbracket 1, d \rrbracket}.
\]
This action of ${S}_d$ commutes with the left action of $G$ on $\KG \backslash \cP^{\times_S d}$.

\medskip

\begin{prop}[\cite{Guignard2018} Proposition 2.32.]\label{prop:symmetric_power_torsor}
If $X$ is Zariski-locally quasi-projective on $S$, then the right action of ${S}_d$ on $\KG \backslash \cP^{\times_S d}$ is admissible,
so that the quotient $\cP^{[d]}$ of $\KG \backslash \cP^{\times_S d}$ by ${S}_d$ exists as a scheme over $S$.
Moreover, the canonical morphism $\cP^{[d]} \to \mathrm{Sym}_S^d(X)$ is a $G$-torsor, 
and the morphism
\[
p_1^{-1}\cP \otimes^G \cdots \otimes^G p_d^{-1}\cP \to r^{-1}\cP^{[d]}
\]
where $r : X^{\times_S d} \to \mathrm{Sym}_S^d(X)$ is the canonical projection, is an isomorphism of $G$-torsors over $X^{\times_S d}$.
\end{prop}

\begin{definition}[Symmetric powers of rank-one local systems]
\label{definition:symmetric_power_local_system}
Let $\Lambda$ be a finite commutative ring, let $G=\Lambda^\times$, and let
$\mathcal{F}$ be a rank-one $\Lambda$-local system on $X$. If
$\mathcal{P}=\operatorname{Fr}(\mathcal{F})$, we define
\[
\mathcal{F}^{[d]}:=\mathcal{P}^{[d]}\times^G\Lambda
\]
on $X^{(d)}$. Equivalently, $\mathcal{P}^{[d]}$ is the frame torsor of
$\mathcal{F}^{[d]}$. By \Cref{prop:symmetric_power_torsor} and the monoidal
compatibility in \Cref{prop:torsor_module_equivalence}, its pullback along
$r:X^{\times_S d}\to X^{(d)}$ satisfies
\[
r^{-1}\mathcal{F}^{[d]}
\cong p_1^{-1}\mathcal{F}\otimes_\Lambda\cdots\otimes_\Lambda
p_d^{-1}\mathcal{F}.
\]
Thus this definition agrees with the usual descent construction of the
symmetric power of a rank-one local system.
\end{definition}
%the $S_d$-action on $\KG \backslash \cP^{\times_S d}$ is compatible with the $S_d$-action on $X^{\times_S d}$, so that we get a canonical morphism $\cP^{[d]} \to \mathrm{Sym}_S^d(X)$.

% %Note that there is a canonical map $\cP^{\times_S d}/S_d \to \cP^$, and the $S_d$-action on $\KG \backslash \cP^{\times_S d}$ is compatible with the $S_d$-action on $X^{\times_S d}$, so that we get a canonical morphism $\cP^{[d]} \to \mathrm{Sym}_S^d(X)$.
% \textcolor{red}{This entire corollary is not exact, replace with: 
% https://gemini.google.com/app/8d257f0b8e6f5927
% or
% https://gemini.google.com/app/f36ed1280d780bea
% }

When $G$ is abelian, and letting the $S_d$-action be a left action (via the inverse), then
the condition  $\prod_{i=1}^d g_i = 1$ defining $\KG$ is invariant under permuting the coordinates.
Therefore, the left action of $S_d$ normalizes the action of $\KG$.
The group generated by these two actions is the semidirect product $\Xi = \KG \rtimes S_d$,
which is a finite group acting on the left on $\cP^d$.
Then the double qoutient $(\KG \backslash \cP^{\times_S d}) / S_d \cong S_d \backslash (\KG \backslash \cP^{\times_S d})$
\textcolor{red}{add here, explain why the qoutineing by the double qoutient exists, should the action be free or something?}
is the same as the quotient $\Xi \backslash \cP^{\times_S d}$, where
$\Xi$ acts on $\cP^{\times_S d}$ by the formula:
$$((g_1, \dots, g_d), \sigma) \star (p_1, \dots, p_d) = (g_1 p_{\sigma^{-1}(1)}, g_2 p_{\sigma^{-1}(2)}, \dots, g_d p_{\sigma^{-1}(d)})$$


\begin{cor}\label{cor:sym-power-quotient}
    Under the assumptions of the above discussion, there is a natural canonical morphism 
    $$q: S_d \backslash \cP^{\times_S d} \to \Xi \backslash \cP^{\times_S d}$$
    or equivlantly
    $$ q: S_d \backslash \cP^{\times_S d} \to (\KG \backslash \cP^{\times_S d}) / S_d$$

    between the symmetric power of $\cP$ as a scheme and the symmetric power of $\cP$ as a $G$-torsor.
    We make it a convention to denote the symmetric power of $\cP$ as a scheme by 
    $\cP^{(d)}$, and the symmetric power of $\cP$ as a $G$-torsor by $\cP^{[d]}$. 
    So that the above qoutient map is also written as:
    $q: \cP^{(d)} \to \cP^{[d]}$.
\end{cor}

\begin{proof}
    $S_d$ is a subgroup of $\Xi$,
    hence any map that is $\Xi$-invariant is automatically $S_d$-invariant.
\end{proof}

\begin{rem*}
    Note that the above discussion does not require that $\cP$ is a $G$-torsor over $X$, only that it is a scheme
    with a left $G$-action.
\end{rem*}



%
% QUOTIENT OF TORSORS TOWERS
%
\subsection*{Quotient of Torsors Towers}
\phantomsection\label{subsection:quotient_torsors_towers}

We now study how the symmetric power construction of \Cref{prop:symmetric_power_torsor} interacts with the canonical decomposition of \Cref{prop:quotient_torsors_finite}.
Throughout this subsection, $G$ denotes a finite abelian group, $H \subseteq G$ a subgroup, and $\cP \to X$ a $G$-torsor over an $S$-scheme $X$ that is Zariski-locally quasi-projective over $S$.
Recall that $\cP \to X$ factors canonically as
\[
\cP \xrightarrow{\phi} \cP_{G/H} \xrightarrow{\psi} X,
\]
where $\cP_{G/H} = \cP \times^G (G/H)$ is a $G/H$-torsor over $X$ and $\phi$ is an $H$-torsor.

In addition to the kernel $\KG = \ker(G^d \to G)$ of the summation morphism appearing in \Cref{prop:symmetric_power_torsor}, we shall need the analogous \emph{summation kernels}
\[
K_H := \ker(H^d \to H), \qquad K_{G/H} := \ker((G/H)^d \to G/H).
\]
Applying the snake lemma to the commutative diagram
\[
\begin{tikzcd}[row sep=large, column sep=large]
0 \arrow[r] & H^d \arrow[r] \arrow[d, twoheadrightarrow] & G^d \arrow[r] \arrow[d, twoheadrightarrow] & (G/H)^d \arrow[r] \arrow[d, twoheadrightarrow] & 0 \\
0 \arrow[r] & H \arrow[r] & G \arrow[r] & G/H \arrow[r] & 0,
\end{tikzcd}
\]
in which the vertical maps are the surjective summation morphisms, yields a short exact sequence
\begin{equation}\label{eq:summation_kernels_ses}
0 \to K_H \to \KG \to K_{G/H} \to 0.
\end{equation}
The induced isomorphism $\KG/K_H \cong K_{G/H}$ will play a central role below.

We define four quotient schemes
\begin{align*}
    \cP^{[d]_G} &:= (\KG \rtimes S_d) \backslash \cP^{\times_S d}, \\
    \cP^{[d]_H} &:= (K_H \rtimes S_d) \backslash \cP^{\times_S d}, \\
    (\cP_{G/H})^{(d)} &:= (H^d \rtimes S_d) \backslash \cP^{\times_S d}, \\
    (\cP_{G/H})^{[d]} &:= ((H^d + \KG) \rtimes S_d) \backslash \cP^{\times_S d},
\end{align*}
where $S_d$ acts on $\cP^{\times_S d}$ as in \Cref{cor:sym-power-quotient} and the subgroups $K_H \subseteq \KG \subseteq H^d + \KG$ and $H^d \subseteq H^d + \KG$ of $G^d$ act diagonally on $\cP^{\times_S d}$ via the $G$-action on $\cP$. The first space is the symmetric $G$-power of $\cP$ as in \Cref{prop:symmetric_power_torsor}; the remaining three are, respectively, the symmetric $H$-power of $\cP$ relative to $\phi$, the symmetric power of the scheme $\cP_{G/H}$, and the symmetric $G/H$-power of $\cP_{G/H}$.
\textcolor{red}{\textbf{The latter two identifications follow from $(\cP_{G/H})^{\times_S d} \cong H^d \backslash \cP^{\times_S d}$ together with the fact that the preimage of $K_{G/H} \subseteq (G/H)^d$ under $G^d \twoheadrightarrow (G/H)^d$ equals $H^d + \KG$.}}
\textcolor{red}{the last isomorphism like that, is from the correspondence theorem, claude generated at the end of the article, add it somewhere}

\begin{prop}\label{prop:torsor_tower_diagram}
The four quotient schemes above exist and fit into a canonical commutative diagram
\[
\begin{tikzcd}[row sep=large, column sep=large]
    \cP^{[d]_H} \arrow[r, "H"] \arrow[d] & (\cP_{G/H})^{(d)} \arrow[d, "q"] \\
    \cP^{[d]_G} \arrow[r, "H"'] \arrow[dr, "G"', bend right=20] & (\cP_{G/H})^{[d]} \arrow[d, "G/H"] \\
    & X^{(d)},
\end{tikzcd}
\]
in which each labelled arrow is a torsor under the indicated constant group. The right-hand vertical $q$ is the canonical projection of \Cref{cor:sym-power-quotient}, applied to the $G/H$-torsor $\cP_{G/H} \to X$; in general it is \emph{not} a torsor under any constant group scheme (see the remark below). The unlabelled left-hand vertical $\cP^{[d]_H} \to \cP^{[d]_G}$ is the canonical projection induced by the inclusion of $S_d$-stable subgroups $K_H \rtimes S_d \subseteq \KG \rtimes S_d$ in $G^d \rtimes S_d$; it is the base change of $q$ along the structural map $\cP^{[d]_G} \to (\cP_{G/H})^{[d]}$ via the Cartesian property below, and likewise fails to be a torsor under a constant group scheme in general.

Moreover, the upper square is Cartesian:
\[
\cP^{[d]_H} \cong \cP^{[d]_G} \times_{(\cP_{G/H})^{[d]}} (\cP_{G/H})^{(d)}.
\]
\end{prop}

\begin{proof}
The four labelled arrows are torsors under the indicated constant groups by direct application of \Cref{prop:symmetric_power_torsor} and \Cref{prop:quotient_torsors_finite}:
\begin{itemize}
    \item Applied to the $G$-torsor $\cP \to X$, \Cref{prop:symmetric_power_torsor} gives the $G$-torsor $\cP^{[d]_G} \to X^{(d)}$ (the diagonal arrow).
    \item Applied to the $H$-torsor $\phi: \cP \to \cP_{G/H}$ (taking $\cP_{G/H}$ in place of the base $X$), \Cref{prop:symmetric_power_torsor} gives the $H$-torsor $\cP^{[d]_H} \to (\cP_{G/H})^{(d)}$ (the top arrow).
    \item Applied to the $G/H$-torsor $\psi: \cP_{G/H} \to X$, \Cref{prop:symmetric_power_torsor} gives the $G/H$-torsor $(\cP_{G/H})^{[d]} \to X^{(d)}$ (the bottom-right vertical), and \Cref{cor:sym-power-quotient} produces the canonical morphism $q : (\cP_{G/H})^{(d)} \to (\cP_{G/H})^{[d]}$.
\end{itemize}

The factorization $\cP^{[d]_G} \xrightarrow{H} (\cP_{G/H})^{[d]} \xrightarrow{G/H} X^{(d)}$ of the diagonal arrow into an $H$-torsor followed by a $G/H$-torsor is the canonical decomposition of \Cref{prop:quotient_torsors_finite}, applied to the $G$-torsor $\cP^{[d]_G} \to X^{(d)}$ and the subgroup $H \subseteq G$. 
Indeed, both $\cP^{[d]_G} \times^G (G/H)$ and $(\cP_{G/H})^{[d]}$ are realized as the admissible quotient 
$((H^d + \KG) \rtimes S_d) \backslash \cP^{\times_S d}$.
\textcolor{red}{here maybe add more info, like isomorphism theorem for torsors and qoutients, or something like that, to make it more clear, from which it follows}

To prove the upper square is Cartesian, set $F := \cP^{[d]_G} \times_{(\cP_{G/H})^{[d]}} (\cP_{G/H})^{(d)}$. 
Base-changing the $H$-torsor $\cP^{[d]_G} \to (\cP_{G/H})^{[d]}$ along $q$ exhibits $F$ as an $H$-torsor over $(\cP_{G/H})^{(d)}$. 
The universal property of the fiber product furnishes a canonical morphism $\cP^{[d]_H} \to F$ over $(\cP_{G/H})^{(d)}$, 
which is $H$-equivariant since the $H$-actions on both source and target are induced by the diagonal $H$-action on $\cP^{\times_S d}$ \textcolor{red}{add earlier in the section of torsors that in fact base changing an $H$-torsor along a morphism gives another $H$-torsor
 is a torsor}. 
 Any morphism of $H$-torsors is an isomorphism, so $\cP^{[d]_H} \cong F$ and the upper square is Cartesian. The left vertical $\cP^{[d]_H} \to \cP^{[d]_G}$ is then identified, via this Cartesian square, with the base change of $q$ along $\cP^{[d]_G} \to (\cP_{G/H})^{[d]}$.
\end{proof}

\begin{rem*}
The two vertical morphisms $q : (\cP_{G/H})^{(d)} \to (\cP_{G/H})^{[d]}$ and $\cP^{[d]_H} \to \cP^{[d]_G}$ are not, in general, torsors under any constant group scheme. The obstruction is purely group-theoretic: in $\KG \rtimes S_d$ the subgroup $K_H \rtimes S_d$ is not normal, because the conjugation action of $S_d$ on $\KG$ by coordinate permutation is non-trivial — for $k \in \KG$ and $\sigma \in S_d$, the components of $k - \sigma\!\cdot\!k$ are $k_i - k_{\sigma^{-1}(i)} \in G$, which need not lie in $H$. Equivalently, $H^d \rtimes S_d$ is not normal in $(H^d + \KG) \rtimes S_d$. So the naive set-theoretic quotients $(\KG \rtimes S_d)/(K_H \rtimes S_d)$ and $((H^d + \KG) \rtimes S_d)/(H^d \rtimes S_d)$ are not groups, even though $\KG/K_H \cong K_{G/H}$ and $(H^d + \KG)/H^d \cong K_{G/H}$ as abstract groups.

% A precise description of the structure these morphisms carry would require concepts not introduced in this thesis, namely:
% \begin{itemize}
%     \item the \emph{free locus} $\cP^{[d], \circ} \subseteq \cP^{[d]}$, defined as the preimage of the complement of the big diagonal $\Delta \subseteq X^{(d)}$ (the open locus on which the residual $S_d$-action is free);
%     \item \emph{twisted forms} of a constant finite group, obtained as the contracted product $T \times^{S_d} A$ of an étale $S_d$-torsor $T$ with a finite group $A$ carrying an $S_d$-action; this is a finite étale group scheme, étale-locally isomorphic to the constant group $\underline{A}$ but not globally so when the $S_d$-action on $A$ is non-trivial and $T$ does not split;
%     \item \emph{torsors under non-constant group schemes}, generalising the constant-group torsors used throughout this thesis.
% \end{itemize}
% With these in hand, one shows that, restricted to the free locus, $q$ is a torsor under a twisted form of the constant group $K_{G/H}$, of degree $|K_{G/H}| = |G/H|^{d-1}$; the left vertical inherits the same description by base change. We do not need this refinement in what follows: only the four labelled torsors and the Cartesian property are used.
\end{rem*}

% \Cref{prop:torsor_tower_diagram} encodes two distinct factorizations of $\cP^{[d]_H} \to X^{(d)}$, which we shall refer to as the two \emph{towers}:

% \begin{description}
%     \item[The $H$-symmetric tower,] obtained by traversing the top edge and the right column of the diagram:
%     \[
%     \cP^{[d]_H} \xrightarrow{\;H\;} (\cP_{G/H})^{(d)} \xrightarrow{\;q\;} (\cP_{G/H})^{[d]} \xrightarrow{\;G/H\;} X^{(d)};
%     \]
%     \item[The $G$-symmetric tower,] obtained by traversing the left column and the bottom row of the diagram:
%     \[
%     \cP^{[d]_H} \longrightarrow \cP^{[d]_G} \xrightarrow{\;H\;} (\cP_{G/H})^{[d]} \xrightarrow{\;G/H\;} X^{(d)}.
%     \]
% \end{description}
% In each tower the labelled arrows are torsors under the indicated constant groups; the unlabelled arrow and the morphism $q$ are not, in general, torsors under a constant group scheme.

% The Cartesian property in \Cref{prop:torsor_tower_diagram} expresses that the connection morphism $\cP^{[d]_H} \to \cP^{[d]_G}$ on the left is the base change of $q : (\cP_{G/H})^{(d)} \to (\cP_{G/H})^{[d]}$ along the structural map $\cP^{[d]_G} \to (\cP_{G/H})^{[d]}$. 
% Properties of $q$ that are stable under base change therefore descend automatically to the connection morphism on the left.

%
% COMPATIBILITY WITH ADDITION
%
\subsection*{Compatibility with Addition}
The construction of symmetric powers is compatible with a natural addition law.
For any integers $d_1, d_2 \geq 0$, there exists a canonical \textbf{addition morphism}
\[ +_{d_1, d_2}: X^{(d_1)} \times_S X^{(d_2)} \to X^{(d_1+d_2)} \]
induced by the equivariant isomorphism $X^{\times_S d_1} \times_S X^{\times_S d_2} \cong X^{\times_S (d_1+d_2)}$ with respect to the inclusion of the product of symmetric groups $S_{d_1} \times S_{d_2} \subseteq S_{d_1+d_2}$.

\begin{prop}\label{prop:symmetric_powers_on_curves}
    Let $\cP$ be a $G$-torsor over $X$. There is a canonical isomorphism of $G$-torsors over $X^{(d_1)} \times_S X^{(d_2)}$:
    \[
    +_{d_1, d_2}^{-1} \left( \cP^{[d_1+d_2]} \right) \cong r_1^{-1} \cP^{[d_1]} \otimes^G r_2^{-1} \cP^{[d_2]}.
    \]
\end{prop}
\begin{proof}
Let $\pi = r_{d_1} \times r_{d_2}$. By the commutativity of the following diagram
\[
\begin{tikzcd}
X^{\times_S d_1} \times_S X^{\times_S d_2} \arrow[r, "\sim"] \arrow[d, "\pi"'] & X^{\times_S (d_1+d_2)} \arrow[d, "r_{d_1+d_2}"] \\
X^{(d_1)} \times_S X^{(d_2)} \arrow[r, "+_{d_1, d_2}"] & X^{(d_1+d_2)}
\end{tikzcd}
\]
and applying \Cref{prop:symmetric_power_torsor}, we obtain canonical isomorphisms:
\[
\pi^{-1} \left( +_{d_1, d_2}^{-1} \cP^{[d_1+d_2]} \right) \cong r_{d_1+d_2}^{-1} \cP^{[d_1+d_2]} \cong \sideset{}{^G}\bigotimes_{i=1}^{d_1+d_2} p_i^{-1} \cP
\]
and
\[
\pi^{-1} (r_1^{-1} \cP^{[d_1]} \otimes^G r_2^{-1} \cP^{[d_2]}) \cong \left( \sideset{}{^G}\bigotimes_{i=1}^{d_1} p_i^{-1} \cP \right) \otimes^G \left( \sideset{}{^G}\bigotimes_{j=d_1+1}^{d_1+d_2} p_j^{-1} \cP \right).
\]
Since both pullbacks identify with
\[
\sideset{}{^G}\bigotimes_{k=1}^{d_1+d_2} p_k^{-1} \cP
\]
in an $S_{d_1} \times S_{d_2}$-equivariant manner, the isomorphism descends to the quotient $X^{(d_1)} \times_S X^{(d_2)}$ by \Cref{prop:symmetric_power_flat_base_change}.
\end{proof}
