\section{Local Ramification Preliminaries}
This section reviews the ramification of discrete valuations, beginning with the general theory of \textit{discrete valuation rings} and their 
integral closures in finite separable extensions. 
We then specialize to complete rings in Galois extensions to describe the ramification filtration via lower and upper numbering, 
following the treatments in \stackstag{0EXQ} and \cite{serreLF}.

\begin{definition}[\stackstag{09E4}]\label{definition:weakly_unramified_and_tamely_ramified_DVR}
    We say that $A \to B$ or $A \subset B$ is an extension of discrete valuation rings if $A$ and $B$ are discrete valuation rings and $A \to B$ is injective and local. In particular, if $\pi _ A$ and $\pi _ B$ are uniformizers of $A$ and $B$, then $\pi _ A = u \pi _ B^ e$ for some $e \geq 1$ and unit $u$ of $B$. The integer $e$ does not depend on the choice of the uniformizers as it is also the unique integer $\geq 1$ such that
\[ \mathfrak m_ A B = \mathfrak m_ B^ e \]
The integer $e$ is called the \textit{ramification index} of $B$ over $A$. We say that $B$ is \textit{weakly unramified} over $A$ if $e = 1$. 
If the extension of residue fields $\kappa _ A = A/\mathfrak m_ A \subset \kappa _ B = B/\mathfrak m_ B$ is finite, 
then we set $f = [\kappa _ B : \kappa _ A]$ and we call it the \textit{residual degree} or residue degree of the extension $A \subset B$.

Note that we do not require the extension of fraction fields to be finite.
\end{definition}

Now let $A$ be a discrete valuation ring with fraction field $K$, let  $L/K$ be a finite separable field extension and 
let $B \subset L$ be the integral closure of $A$ in $L$.
% \[ \xymatrix{ B \ar[r] & L \\ A \ar[u] \ar[r] & K \ar[u] } \]
Then the ring extension $A \subset B$ is finite, hence $B$ is Noetherian. 
The dimension of $B$ is $1$, hence $B$ is a Dedekind domain.
Let $\mathfrak m_1, \ldots , \mathfrak m_ n$ be the maximal ideals of $B$ (i.e., the primes lying over $\mathfrak m_ A$). 
We obtain extensions of discrete valuation rings

\[ A \subset B_{\mathfrak m_ i} \]
and hence ramification indices $e_ i$ and residue degrees $f_ i$. We have

\[ [L : K] = \sum \nolimits _{i = 1, \ldots , n} e_ i f_ i \]
Note that if $A$ is henselian (e.g. $A$ is complete) then $n=1$. 

\begin{definition}[\stackstag{09E9}]\label{definition:tamely_ramified_dvrs}
Let $A$ be a discrete valuation ring with fraction field $K$. Let $L/K$ be a finite separable extension. With $B$ and $\mathfrak m_ i$, $i = 1, \ldots , n$ 
as above, we say the extension $L/K$ is
\begin{enumerate}
    \item unramified with respect to $A$ if $e_ i = 1$ and the extension $\kappa (\mathfrak m_ i)/\kappa _ A$ is separable for all $i$,
    \item tamely ramified with respect to $A$ if either the characteristic of $\kappa _ A$ is $0$ or the characteristic of $\kappa _ A$ is $p > 0$, the field extensions $\kappa (\mathfrak m_ i)/\kappa _ A$ are separable, and the ramification indices $e_ i$ are prime to $p$, and
    \item totally ramified with respect to $A$ if $n = 1$ and the residue field extension $\kappa (\mathfrak m_1)/\kappa _ A$ is trivial.
\end{enumerate}
If the discrete valuation ring $A$ is clear from context, then we sometimes say $L/K$ is unramified, totally ramified, or tamely ramified for short.
\end{definition}

% - %
Now and for the rest of the section assume $A$ is a \textit{complete discrete valuation ring} with uniformizer $\pi$ 
and residue field $\kappa$, which we assume to be perfect. When $A$ and $\kappa$ are of the same characteristic $p > 0$, 
then $A$ contains a coefficient field $k \cong \kappa$ and a well known structure theorem holds: $A = k[[\pi ]] \cong k[[t]]$.
Let $K$ be the fraction field of $A$, then $K=k((\pi))$.

For the remainder of this section, assume $A$ is a \textit{complete discrete valuation ring} with uniformizer $\pi$ and a perfect residue 
field $\kappa$. In the equal characteristic case, where $\text{char}(A) = \text{char}(\kappa) = p > 0$, the 
Cohen Structure Theorem implies that $A$ contains a coefficient field $k \cong \kappa$, such that $A \cong k[[\pi]] \cong k[[t]]$. 
Consequently, the fraction field is given by $K = k((\pi))$.
Let $L/K$ be a finite Galois extension with Galois group $G$. 
The integral closure $B$ of $A$ in $L$ is itself a complete discrete valuation ring. 
Since the residue field $\kappa$ is perfect, the extension of residue fields is separable, and there exists a uniformizer 
$\Pi \in B$ such that $B = A[\Pi]$.

The \textit{lower numbering ramification filtration} of $G$, denoted by $(G_i)_{i \geq -1}$, is defined as:
\[ 
G_i = \{ \sigma \in G \mid v_B(\sigma (x) - x) \geq i + 1 \text{ for all } x \in B \} 
\]
where $v_B$ is the valuation on $L$ associated with $B$. In this indexing, $G_{-1} = G$ and $G_0$ 
corresponds to the \textit{inertia group} of the extension $L/K$. Note that $L/K$ is unramified if and only if 
$G_0 = \{1\}$, and it is tamely ramified if and only if $G_1 = \{1\}$.

A standard result in the theory of local fields(complete local fields with a discrete valuation and perfect residue field) 
ensures that the condition in the definition of $G_i$ need only be checked for the uniformizer $\Pi$ of $B$. 
Specifically, if we define the function
\[ 
i^L_K(\sigma) = v_B(\sigma(\Pi) - \Pi) 
\]
for $\sigma \in G$, then $G_i = \{ \sigma \in G \mid i^L_K(\sigma) \geq i + 1 \}$. 
The subgroups $G_i$ are normal in $G$ and become trivial for sufficiently large $i$.

Consider a tower of fields $K \subset E \subset L$, and let $H = \text{Gal}(L/E) \subset G$. The lower numbering is compatible with subgroups:
\[ 
G_i \cap H = H_i \quad \text{for all } i \geq -1 
\]
which follows from the identity $i^L_E = i^L_K|_{H}$. 
However, the lower numbering does not behave as simply with respect to quotients. If $H$ is normal in $G$, the image of $G_i$ in $G/H$ is generally not $(G/H)_i$. 
Instead, we have $G_i H / H = (G/H)_j$, where the index $j$ is given by the formula:
\[ 
j = \frac{1}{e_{L/E}} \sum_{\tau \in H} \min(i^L_K(\tau), i+1) - 1 
\]


In the literature, one reindexes the ramification groups by defining the Herbrand function $\phi_{L/K} : [-1, \infty ) \to [-1, \infty )$:
\[ \phi_{L/K}(i) = \frac{1}{e_{L/K}}\sum_{\sigma \in G} \min(i^L_K(\sigma), i+1)-1 = \int _0^i \frac{1}{[G_0 : G_t]} dt \]

This function is continuous, strictly increasing, and piecewise linear, making it a bijection. 
It satisfies the composition law $\phi_{L/K} = \phi_{E/K} \circ \phi_{L/E}$ for a tower of extensions $K \subset E \subset L$. 
Using this function, we define the \textit{upper numbering ramification groups} as:
\[ 
G^i = G_{\phi_{L/K}^{-1}(i)} 
\]
The primary advantage of this reindexing is its compatibility with quotients: for any normal subgroup $H \subset G$, we have:
\[ 
G^i H / H = (G/H)^i 
\]
for all $i \geq -1$.


%% [REVIEW: never used -- the structure of G_i/G_{i+1} is not invoked anywhere (tameness is always derived via Kummer/Artin-Schreier); consider deleting or reducing to a one-sentence remark]
\begin{prop}[\Cite{serreLF}, IV Corollary 3]
    the quotients $G_i/G_{i+1}$, $i \geq 1$, are abelian groups, and are direct products of cyclic groups of order $p$. 
    The group $G_1$ is a $p$-group.
\end{prop}


%% [REVIEW: never used -- same as the proposition above; nothing downstream uses the semi-direct product structure of G_0]
\begin{prop}[\Cite{serreLF}, IV Corollary 4]
    The inertia group $G_0$ has the following property:
    \textit{It is the semi-direct product of a cyclic group of order prime to $p$ with a normal subgroup whose order is a power of $p$.}
\end{prop}

% We deduce the following lemma, that will be helpful later:
% \begin{lemma}
% Let $L/K$ be finite galois extesntion with galois group $G=\Z/p^r\Z$
% Assume there exists intermediate local field $K < M < L$ such that $M/K$ is unramified.
% Then $L/K$ is unramified.
% \end{lemma}




\subsection*{Kummer and Artin-Schreier Theories}
For cyclic extensions, Kummer and Artin-Schreier theories provide explicit ways to calculate ramification. 
These results show how the valuation of a defining element $a \in K$ determines the ramification index and the jumps in the upper numbering filtration.
Throughout this section, let $K$ be a discrete valuation field with a perfect residue field $\kappa$ of characteristic $p > 0$.

\begin{theorem}[Ramification in Kummer Extensions, \cite{koch1997algebraic}, Proposition 1.83]\label{theorem:kummer_ramification}
%Let $K$ be a local field of characteristic $\text{char}(K) =p$  
Assume $K$ contains the $n$-th roots of unity $\mu_n$. 
Let $L/K$ be the extension given by the equation $X^n = a$ for some 
$a \in K^\times$ and denote by $G$ its Galois group. Then we have:

\begin{enumerate}
    \item If $v_K(a) \in n\mathbb{Z}$ and the image of $a\pi^{-v_K(a)}$ in the residue field $\kappa$ is an $n$-th power, the extension $L/K$ is trivial.
    \item If $v_K(a) \in n\mathbb{Z}$ and the image of $a\pi^{-v_K(a)}$ in the residue field $\kappa$ is not an $n$-th power, the extension $L/K$ is cyclic and unramified.
    \item If $v_K(a) \notin n\mathbb{Z}$, the extension $L/K$ is cyclic and ramified. Specifically, if $\gcd(|v_K(a)|, n) = 1$, the extension is totally ramified of degree $n$.
     Otherwise it has ramification index $\frac{n}{|gcd(v_K(a)|, n)}$
\end{enumerate}
Conversly, Kummer theory ensures that every cyclic extension of degree $n$, prime to $p$ of a field that contains $n$-th roots of unity, is of the above form.
Moreover, in the above we can always take $a \in \Oo_K$
\end{theorem}
Note that in the case of total ramification the extesntion is tamely ramified.


\begin{theorem}[Ramification in Artin-Schreier Extensions, \cite{Thomas2005}]\label{theorem:artin_schreier_ramification}
Let $\wp(x) = x^p - x$ be the Artin-Schreier opeartor.
Let $L/K$ be the extension given by the equation $X^p - X = a$ for some $a \in K$ and denote by $G$ its Galois group. 
Then we have:
\begin{enumerate}
    \item If $v_K(a) > 0$ or if $v_K(a) = 0$ and $a \in \wp(K)$, the extension $L/K$ is trivial.
    \item If $v_K(a) = 0$ and if $a \notin \wp(K)$, the extension $L/K$ is cyclic of degree $p$ and unramified.
    \item If $v_K(a) = -m < 0$ with $m \in \mathbb{Z}_{>0}$ and if $m$ is prime to $p$, the extension $L/K$ is cyclic of degree $p$ again and totally ramified. Moreover,
     its ramification groups are given by:
     $$G = G^{(-1)} = \dots = G^{(m)} \quad \text{and} \quad G^{(m+1)} = 1.$$
\end{enumerate}
Conversely, Artin-Schreier theory ensures that every cyclic extension of degree $p$ takes this form.
Moreover, in the above and under the isomorphism $K \cong k((t))$, one can always take $a$ of the form 
$c t^{-m} + a_{-m + 1} t^{-m + 1} + \cdots a_{-1}t^{-1} + a_0$. If $k$ is algebraically closed then there is a 
change of variables such that $a=u^{-m}$.
\end{theorem}



%%%% %%%% %%%% %%%% %%%% %%%% %%%% %%%%
%          WITT VECTORS
%%%% %%%% %%%% %%%% %%%% %%%% %%%% %%%%
\input{witt/WittVectorPrerequisites.tex}

%%%% %%%% %%%% %%%% %%%% %%%% %%%% %%%%
%          ALGEBRAIC GEOMETRY
%%%% %%%% %%%% %%%% %%%% %%%% %%%% %%%%
\section{Algebraic Geometry}
In this section we group together some general theorems in algebraic geometry that we will be employing throughtout the text. 
All schemes are assumed to be locally of finite type. 
%% [REVIEW: never cited despite having a full proof -- likely needed when applying lemma:descend_ramification_along_etale (f(xi_X)=xi_Y hypotheses); add a label and cite it at those applications, or remove]
\begin{theorem}
    Let $f:X \to Y$ be a finite flat map between integral schemes, of finite type over a field $k$. if $Z \subset X$ is a prime divisor with generic point $\eta_Z$, then $f(Z) \subset X$
    is a prime divisor with generic point $\eta_{f(Z)}$ satisfying $f(\eta_Z)= \eta_{f(Z)}$
\end{theorem}
\begin{proof}
    $f$ is finite hence proper hence closed so $f(Z)$ is closed subset of $Y$, it is irreducible as the image of an irreducible.
    Since $Z = \overline{\{ \eta_Z \}}$ we get: 
    $$\{f(\eta_Z)\} \subset f(Z) = f(\overline{\{\eta_Z\}}) \subseteq \overline{f(\{\eta_Z\})} = \overline{\{f(\eta_Z)\}}$$
    And since $f(Z)$ is closed we get $f(Z) = \overline{\{f(\eta_Z)\}}$.

    For flat map of integral schemes we have for every $x \in X$, $y=f(x)$ the dimension formula:
    $$\text{dim}(\mathcal{O}_{X,x}) = \text{dim}(\mathcal{O}_{Y,y}) + \text{dim}(\mathcal{O}_{X_y, x})$$
    And since $\text{dim}(\mathcal{O}_{X_y, x}) = 0$ we get $\text{dim}(\mathcal{O}_{X,x}) = \text{dim}(\mathcal{O}_{Y,y})$
    concluding that $f(Z)$ is a prime divisor as well. 
\end{proof}

A known theorem states that: 
\begin{theorem}\label{theorem:int_geoint_implies_productint}
    Let $X, Y$ be two integral schemes over a field $k$. If $X$ is geometrically integral then $X \times_k Y$ 
    is integral.
    If both $X,Y$ are geometrically integral, then $X \times_k Y$ is geometrically integral. 
\end{theorem}

%% [REVIEW: unlabeled & never cited -- smoothness/integrality of C^{(d)} is assumed silently throughout (e.g. RamificationAfterBlowupIsTame ~184, blowup integrality); add a label and cite it. Note: the proof environment is nested inside the theorem environment]
\begin{theorem}
    Let $C$ be smooth projective curve geometrically connected over a field $k$. Then:
    \begin{enumerate}
        \item $C^{(d)}$ is smooth
        \item For every $d$, $C^{(d)}$ is integral.
        \item For every $d$, $C^{(d)}$ is geometrically integral.
        \item The product of every finite number of $C^{(d)}$ is geometrically integral. 
    \end{enumerate}
    \begin{proof}
        \begin{enumerate}
            \item Let $t_i$ be a local parameter for $C$ at $P_i$. The local ring of the product $C^d$ at the point $(P_1, \dots, P_d)$ is isomorphic $k[[t_1, t_2, \dots, t_d]]$
            and the local ring of the qoutient at the divisor $D=\sum P_i$ is $k[[t_1, \dots, t_d]]^{S_d}$ which is 
            isomorphic to $k[[t_1, \dots, t_d]]^{S_d} \cong k[[s_1, \dots, s_d]]$ where the $s_i$ are the 
            symmetric polynomials, hence this ring is regular local ring. 
            \item $C$ is irreducible hence $C^{d}$ is irreducible hence $C^{(d)}$ is irreducible. Since $C^{(d)}$ 
            is smooth it is reduced.
            \item By \stackstag{0366}, $C$ is geometrically integral, so it follows from the above. 
            \item \Cref{theorem:int_geoint_implies_productint}
        \end{enumerate}
    \end{proof}
\end{theorem}


\subsection*{Blowups}

%% [REVIEW: never cited by label -- invoked implicitly as 'blowups commute with flat base change' (RamificationAfterBlowupIsTame:432, GeometricClassFieldTheory:338); add a label and \Cref it there]
\begin{theorem}[\stackstag{0805}]
Let $X_1 \to X_2$ be a flat morphism of schemes. Let $Z_2 \subset X_2$ be a closed subscheme. Let $Z_1$ be the inverse image of $Z_2$ in $X_1$. Let $X'_ i$ be the blowup of $Z_ i$ in $X_ i$. Then there exists a cartesian diagram

\[ \xymatrix{ X_1' \ar[r] \ar[d] & X_2' \ar[d] \\ X_1 \ar[r] & X_2 } \]
of schemes.   
\end{theorem}

%% [REVIEW: never cited in the included text -- only used in sections/GeometricCFT/ExtensionOfTamelyRamifiedSheaf.tex, which is currently not \input anywhere; keep only if that file gets included]
\begin{theorem}
If $X$ is integral then $Bl_Z(X)$ is integral. %This can be checked locally
\end{theorem}


If $X$ is a smooth curve, we have the following result regarding its symmetric power:
%% [REVIEW: unlabeled & never cited -- smoothness of the symmetric power is background used silently (Abel-Jacobi section, Takeuchi compactification); add a label and cite it, or drop the long proof]
    \begin{prop}
        Let $f: X \to S$ be a smooth morphism of relative dimension 1.
        Suppose $f$ is flat and Zariski-locally quasi-projective.
        Then the relative symmetric power $X_S^{(d)} = \text{Sym}^d_S(X)$ is smooth over $S$ of relative dimension $d$.
    \end{prop}
    
    \begin{proof}Since $f: X \to S$ is smooth, the $d$-fold product $X_S^d$ is smooth over $S$. By \Cref{prop:symmetric_power_flat_base_change}, the quotient $X_S^{(d)}$ is flat over $S$. Smoothness is a fiberwise property for flat morphisms of finite presentation (cf. \stackstag{01V8}); thus, it suffices to verify the smoothness of the fibers. 
        For every $s \in S$, the fiber of the symmetric power is given by:$$(\text{Sym}^d_S(X))_s \cong \text{Sym}^d_{\kappa(s)}(X_s)$$Consequently, we may reduce to the case where $S = \text{Spec}(k)$ for a field $k$. 
        Since smoothness is preserved under  base change to the algebraic closure, we may further assume $k = \bar{k}$.
        Let $z = \sum_{i=1}^{r} d_i \cdot x_i \in X^{(d)}$ be a point represented by an effective cycle of degree $d$, where the points $x_i \in X(k)$ are distinct and $\sum d_i = d$. Choose pairwise disjoint Zariski-open subsets $U_i \subset X$ such that $x_i \in U_i$. Let $W \subset X^{(d)}$ be the open subset consisting of cycles whose support is contained in $\bigcup U_i$ and which meet each $U_i$ with degree exactly $d_i$. There is a canonical isomorphism:
$$W \cong \prod_{i=1}^r U_i^{(d_i)}$$
Thus, it suffices to show that each $U_i^{(d_i)}$ is smooth of dimension $d_i$ at the point $d_i \cdot x_i$. 

We may therefore restrict our attention to the "worst" case: the diagonal point $z = d \cdot x$. Let $R = \mathcal{O}_{X,x}$ be the local ring of the curve at $x$. Since $X$ is a smooth curve over $k$, $R$ is a regular local ring of dimension 1, i.e., a discrete valuation ring. Its completion is $\hat{R} \cong k[[t]]$. The completed local ring of the product $X^d$ at the point $(x, \dots, x)$ is:
$$\hat{\mathcal{O}}_{X^d, (x, \dots, x)} \cong \hat{R} \hat{\otimes}_k \dots \hat{\otimes}_k \hat{R} \cong k[[t_1, \dots, t_d]]$$
where $t_i$ is the uniformizer for the $i$-th copy of $X$. The symmetric group $S_d$ acts on this power series ring by permuting the variables 
$t_i$. By the \textit{Fundamental Theorem of Symmetric Polynomials}, the ring of invariants is:
$$\left( k[[t_1, \dots, t_d]] \right)^{S^d} = k[[e_1, \dots, e_d]]$$
where $e_j$ is the $j$-th elementary symmetric power series in the variables $t_i$.

The ring $k[[e_1, \dots, e_d]]$ is a formal power series ring in $d$ variables. A fundamental theorem in commutative algebra states that a local ring is regular if and only if its completion is a formal power series ring over a field. Since $\hat{\mathcal{O}}_{X^{(d)}, z} \cong k[[e_1, \dots, e_d]]$, the local ring $\mathcal{O}_{X^{(d)}, z}$ is a regular local ring of dimension $d$. This implies that $X^{(d)}$ is smooth over $k$ of dimension $d$, completing the proof.
\end{proof}

\subsection*{A Base-Change Lemma for Galois Extensions}

Finally, we record a standard base-change lemma for Galois field extensions, used when
comparing a Galois extension with the function field of a base change.

\begin{lemma}\label{lem:galois-base-change}
Let $E/F$ be a finite Galois extension with group $H$, and let $K/F$ be an arbitrary
field extension. Fix a common overfield $\Omega \supseteq E,K$ (for instance an algebraic
closure of $K$ together with an $F$-embedding $E \hookrightarrow \Omega$), and form inside
it the intersection $M := E \cap K$, the compositum $E\cdot K$, and the subgroup
$N := \Gal(E/M) \leq H$. Then
\begin{enumerate}
  \item $E\cdot K / K$ is Galois, and restriction is an isomorphism
        $\Gal(E\cdot K/K) \xrightarrow{\ \sim\ } \Gal(E/M) = N$; and
  \item as $K$-algebras,
        $\displaystyle E \otimes_F K \;\cong\; \prod_{i=1}^{[M:F]} E\cdot K$.
\end{enumerate}
In particular $E\otimes_F K$ is a field if and only if $M = F$, i.e.\ if and only if $E$ and
$K$ are linearly disjoint over $F$.
\end{lemma}

\begin{proof}
Write $E = F[\alpha]$ and let $g \in F[x]$ be the minimal polynomial of $\alpha$, so
$\deg g = |H|$ and $g$ splits completely in $E$ because $E/F$ is Galois. Part (1) is the
classical translation theorem: $E\cdot K/K$ is Galois (it is generated over $K$ by the
roots of the separable $g$, which all lie in $E$), and $\sigma \mapsto \sigma|_E$ embeds
$\Gal(E\cdot K/K)$ into $H$ with image the subgroup fixing $E\cap K = M$ pointwise, namely
$\Gal(E/M) = N$. For (2), factor $g = g_1 \cdots g_m$ into monic irreducibles over $K$.
Adjoining any single root of $g$ to $K$ already produces all of $E\cdot K$ (since
$E = F(\alpha)$ contains every conjugate of $\alpha$), so each $g_i$ has degree
$[E\cdot K : K] = [E:M] = |N|$ by (1); hence $m = |H|/|N| = [M:F]$. Therefore
\[
E \otimes_F K \;\cong\; K[x]/(g) \;\cong\; \prod_{i=1}^{m} K[x]/(g_i)
\;\cong\; \prod_{i=1}^{[M:F]} E\cdot K ,
\]
the last step because $K[x]/(g_i) \cong K(\alpha) = E\cdot K$ for every $i$. This product is
a single field exactly when $m = 1$, i.e.\ when $[M:F] = 1$, i.e.\ when $M = F$.
\end{proof}

